---
title: "`r params$title`"
output: word_document
params:
  title: ""
  project_ref: ""
  report_month: ""
  report_start: ""
  report_end: ""
  analysis_date: ""
  username: ""

  data_summary: !r NULL

  availability_by_idf: !r NULL
  availability_plot_cal: !r NULL
  availability_plot_freq: !r NULL

  richness_dt: !r NULL
  richness_plot: !r NULL

  curtl_by_species_dt: !r NULL
  curtl_by_group_dt: !r NULL

  short_track_summary_dt: !r NULL

  assess_by_status: !r NULL
  assess_by_turbine: !r NULL

  shutdown_by_turbine: !r NULL
  shutdown_bands: !r NULL
  shutdown_plot: !r NULL

  safe_dist_overall: !r NULL
  safe_dist_by_species: !r NULL
  safe_dist_plot: !r NULL

  id_risk_by_direction: !r NULL
  id_confusion_general: !r NULL

  flight_speed_by_species: !r NULL
  flight_height_by_species: !r NULL
  flight_metrics_plot: !r NULL

  min_indiv_summary: !r NULL
  min_indiv_daily_plot: !r NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Mesmo helper de formatacao de tabelas do report_template.rmd, para manter
# o estilo visual consistente entre o relatorio geral e o mensal.
report_table <- function(x, caption = NULL) {
  ft <- flextable::flextable(as.data.frame(x)) |>
    flextable::theme_box() |>
    flextable::bg(part = "header", bg = "gray85") |>
    flextable::bold(part = "header") |>
    flextable::fontsize(size = 9, part = "header") |>
    flextable::fontsize(size = 9, part = "body") |>
    flextable::align(align = "center", part = "header") |>
    flextable::valign(valign = "center", part = "all") |>
    flextable::autofit()
  if (!is.null(caption)) ft <- flextable::set_caption(ft, caption)
  ft
}
```

**`r params$project_ref`**

Monthly report: `r params$report_month`
Report period: `r params$report_start` to `r params$report_end`
Analysis date: `r params$analysis_date`
Technician: `r params$username`

This report is descriptive: it presents the metrics produced by the IDF analysis pipeline for the month above, without further interpretation, except where an explicit threshold (KNE safe-distance reference line, shutdown-time bands) is already part of the agreed methodology.

---

# 1. Data Universe and Time Span

Row counts and date range of each dataset used in this report, restricted to the month above (SCADA row count restricted to the SCADA-availability window intersected with the month).

```{r data-summary-table}
if (!is.null(params$data_summary)) report_table(params$data_summary)
```

# 2. System Availability (Heartbeats)

Daylight-time availability of IDF units, based on heartbeat signals.

```{r availability-table}
if (!is.null(params$availability_by_idf)) report_table(params$availability_by_idf)
```

```{r availability-cal, fig.width=9, fig.height=4}
if (!is.null(params$availability_plot_cal)) print(params$availability_plot_cal)
```

```{r availability-freq, fig.width=6, fig.height=3}
if (!is.null(params$availability_plot_freq)) print(params$availability_plot_freq)
```

# 3. Observed Species

Number of distinct species classifications recorded within the same track (species richness per track), for tracks recorded in this month.

```{r richness-table}
if (!is.null(params$richness_dt)) report_table(params$richness_dt)
```

```{r richness-plot, fig.width=6, fig.height=4}
if (!is.null(params$richness_plot)) print(params$richness_plot)
```

# 4. Curtailments by Species

Curtailment events triggered in this month, by species and by species group (priority / nonpriority / other / uncategorized).

```{r curtl-species-table}
if (!is.null(params$curtl_by_species_dt)) report_table(params$curtl_by_species_dt)
```

```{r curtl-group-table}
if (!is.null(params$curtl_by_group_dt)) report_table(params$curtl_by_group_dt)
```

# 5. Short-Track Curtailments

Curtailments triggered by tracks with few recorded points, within the evaluation distance range agreed for this metric.

```{r short-track-table}
if (!is.null(params$short_track_summary_dt)) report_table(params$short_track_summary_dt)
```

# 6. Curtailment Response Assessment

Whether SCADA-recorded RPM dropped as expected in response to curtailment signals (tight baseline tolerance), for the turbines and window with SCADA coverage this month.

```{r assess-status-table}
if (!is.null(params$assess_by_status)) report_table(params$assess_by_status)
```

```{r assess-turbine-table}
if (!is.null(params$assess_by_turbine)) report_table(params$assess_by_turbine)
```

# 7. Shutdown Time

Time from curtailment signal to reaching each RPM threshold, by turbine. Bands below/above the agreed cut-offs are reported as-is, without further interpretation.

```{r shutdown-turbine-table}
if (!is.null(params$shutdown_by_turbine)) report_table(params$shutdown_by_turbine)
```

```{r shutdown-bands-table}
if (!is.null(params$shutdown_bands)) report_table(params$shutdown_bands)
```

```{r shutdown-plot, fig.width=7, fig.height=6}
if (!is.null(params$shutdown_plot)) print(params$shutdown_plot)
```

# 8. Safe Distance (KNE Methodology)

Distance between the triggering track and the turbine at the moment of curtailment, compared against the KNE reference line, by priority species.

```{r safe-dist-overall-table}
if (!is.null(params$safe_dist_overall)) report_table(params$safe_dist_overall)
```

```{r safe-dist-species-table}
if (!is.null(params$safe_dist_by_species)) report_table(params$safe_dist_by_species)
```

```{r safe-dist-plot, fig.width=8, fig.height=8}
if (!is.null(params$safe_dist_plot)) print(params$safe_dist_plot)
```

# 9. Bi-Directional ID Transitions

Curtailments triggered by a species reclassification within the same track, in both directions (priority-to-nonpriority and nonpriority-to-priority), and the species most frequently confused with the species of interest within the same track.

```{r id-risk-table}
if (!is.null(params$id_risk_by_direction)) report_table(params$id_risk_by_direction)
```

```{r id-confusion-table}
if (!is.null(params$id_confusion_general)) report_table(params$id_confusion_general)
```

# 10. Biological Flight Metrics

Flight speed and flight height per species, for tracks meeting the quality filters agreed for this metric.

```{r flight-speed-table}
if (!is.null(params$flight_speed_by_species)) report_table(params$flight_speed_by_species)
```

```{r flight-height-table}
if (!is.null(params$flight_height_by_species)) report_table(params$flight_height_by_species)
```

```{r flight-metrics-plot, fig.width=8, fig.height=6}
if (!is.null(params$flight_metrics_plot)) print(params$flight_metrics_plot)
```

# 11. Minimum Individuals per Time Bin

Minimum number of distinct individuals per priority species detected in the same time bin, farm-wide, summarised by day.

```{r min-indiv-summary-table}
if (!is.null(params$min_indiv_summary)) report_table(params$min_indiv_summary)
```

```{r min-indiv-daily-plot, fig.width=8, fig.height=6}
if (!is.null(params$min_indiv_daily_plot)) print(params$min_indiv_daily_plot)
```

# Annexes

The full detail behind each table above (including all rows, not only the summaries shown here) is provided as separate files in the same output folder as this report, one workbook/plot set per section: data summary, system availability, observed species, curtailments by species, short-track curtailments, curtailment response assessment, shutdown time, safe distance, ID transitions and species confusion, biological flight metrics, and minimum individuals per bin.
