---
title: "`r params$title`"
output:
  officedown::rdocx_document:
    page_size:
      width: 8.27
      height: 11.69
      orient: "portrait"
      unit: "in"
params:
  title: ""
  project_ref: ""
  report_month: ""
  report_start: ""
  report_end: ""
  analysis_date: ""
  username: ""

  data_summary: !r NULL
  coverage_summary: !r NULL
  coverage_plot: !r NULL

  availability_by_idf: !r NULL
  availability_plot_cal: !r NULL
  availability_plot_freq: !r NULL
  availability_plot_spatial: !r NULL

  richness_dt: !r NULL
  richness_plot: !r NULL

  curtl_by_species_dt: !r NULL
  curtl_by_group_dt: !r NULL

  short_track_summary_dt: !r NULL

  assess_by_status: !r NULL
  assess_by_turbine: !r NULL

  shutdown_by_turbine: !r NULL
  shutdown_bands: !r NULL
  shutdown_plot: !r NULL

  safe_dist_overall: !r NULL
  safe_dist_by_species: !r NULL
  safe_dist_plot: !r NULL

  id_risk_by_direction: !r NULL
  id_confusion_species: !r NULL
  id_confusion_general: !r NULL

  flight_speed_by_species: !r NULL
  flight_height_by_species: !r NULL
  flight_metrics_plot: !r NULL

  min_indiv_summary: !r NULL
  min_indiv_daily_plot: !r NULL

  # Literais de configuracao (monthlyReportSettings.R) usados so' para
  # texto descritivo -- cada secção que aplica um threshold/cut-off mostra
  # o VALOR concreto usado nesse mes, nao so' o nome do parametro.
  heartbeat_interval_min: !r NULL
  heartbeat_offline_gap_min: !r NULL
  idf_availability_top_n: !r NULL

  shorttrack_min_points: !r NULL
  shorttrack_eval_range_m: !r NULL

  curtailment_start_end_gap_sec: !r NULL
  curtailment_max_next_gap_sec: !r NULL
  curtailment_drop_pct_threshold: !r NULL
  safe_shutdown_rpm: !r NULL

  shutdown_time_low_cut: !r NULL
  shutdown_time_high_cut: !r NULL

  safe_dist_reference_line_m: !r NULL
  safe_dist_rpm_threshold: !r NULL
  safe_dist_already_slowing_rpm: !r NULL

  id_transition_late_time_sec: !r NULL
  track_proximity_threshold_m: !r NULL

  flight_min_track_points: !r NULL
  flight_speed_ms_min: !r NULL
  flight_speed_ms_max: !r NULL
  riskHeight_lower: !r NULL
  riskHeight_upper: !r NULL

  min_individuals_bin_min: !r NULL
  min_individuals_merge_dist_m: !r NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Mesmo helper de formatacao de tabelas do report_template.rmd, para manter
# o estilo visual consistente entre o relatorio geral e o mensal.
report_table <- function(x, caption = NULL) {
  ft <- flextable::flextable(as.data.frame(x)) |>
    flextable::theme_box() |>
    flextable::bg(part = "header", bg = "gray85") |>
    flextable::bold(part = "header") |>
    flextable::fontsize(size = 9, part = "header") |>
    flextable::fontsize(size = 9, part = "body") |>
    flextable::align(align = "center", part = "header") |>
    flextable::valign(valign = "center", part = "all") |>
    flextable::autofit()
  if (!is.null(caption)) ft <- flextable::set_caption(ft, caption)
  ft
}
```

<!--
Cada tabela/plot abaixo tem, imediatamente acima do chunk que a produz, um
comentario "Source: ..." a apontar para a funcao R (e ficheiro) que calcula
o objeto correspondente em IDF_monthly_report.R -- usar isso para encontrar
rapidamente onde ajustar cada tabela/plot (colunas, arredondamento, filtros,
etc.) sem ter de procurar pelo nome do param em todo o script. Estes
comentarios HTML nao aparecem no .docx gerado.

Cada tabela/plot tem tambem a sua propria subsecção (##), com 1 frase a
identificar o objeto, mesmo quando 2 tabelas pertencem à mesma secção
(ex: 6.1/6.2) -- isto e' deliberado: 2 flextables em chunks consecutivos
sem nenhum paragrafo de texto a separa-los tendem a sair "coladas" no docx
(dificeis de selecionar/mover/editar independentemente no Word). Uma frase
de texto entre elas garante uma quebra de paragrafo real a separa-las.
-->

**`r params$project_ref`**

Monthly report: `r params$report_month`
Report period: `r params$report_start` to `r params$report_end`
Analysis date: `r params$analysis_date`
Technician: `r params$username`

This report is descriptive: it presents the metrics produced by the IDF analysis pipeline for the month above, without further interpretation, except where an explicit threshold (KNE safe-distance reference line, shutdown-time bands) is already part of the agreed methodology.

---

# 1. Data Universe and Time Span

## 1.1 Row Counts and Date Range

Row counts and date range of each dataset used in this report, restricted to the month above (SCADA row count restricted to the SCADA-availability window intersected with the month).

<!-- Source: monthly_data_summary_dt <- summarise_dataset_extent(), R/dataset_summary.R (called from IDF_monthly_report.R, section "0. Data extent / quantities table") -->
```{r data-summary-table}
if (!is.null(params$data_summary)) report_table(params$data_summary)
```

## 1.2 Temporal Coverage

Day-by-day data presence for each dataset within the month -- complements 1.1, which only gives the overall min/max/row count and does not show whether there are gaps within that range.

<!-- Source: monthly_coverage_summary_dt <- data_coverage_summary(); p_monthly_coverage <- plot_data_coverage(monthly_coverage_calendar_dt <- data_coverage_calendar()), all R/data_coverage.R -->
```{r coverage-summary-table}
if (!is.null(params$coverage_summary)) report_table(params$coverage_summary)
```

```{r coverage-plot, fig.width=7, fig.height=4}
if (!is.null(params$coverage_plot)) print(params$coverage_plot)
```

# 2. System Availability (Heartbeats)

Heartbeats are expected every `r params$heartbeat_interval_min` minutes; an IDF unit is considered offline once the gap since its last heartbeat exceeds `r params$heartbeat_offline_gap_min` minutes (at least 2 consecutive heartbeats missed).

## 2.1 Availability by IDF Unit

Total offline time and daylight-availability category for each IDF unit, this month.

<!-- Source: idf_availability_summary$by_idf <- summarise_availability(idf_availability_dt), R/availability_daylight.R (idf_availability_dt itself from daylight_availability()) -->
```{r availability-table}
if (!is.null(params$availability_by_idf)) report_table(params$availability_by_idf)
```

## 2.2 Availability Calendar

Daily offline percentage per IDF unit, laid out as a calendar (top `r params$idf_availability_top_n` units by offline time only, to stay legible).

<!-- Source: plot_availability_calendar(), R/availability_daylight.R -->
```{r availability-cal, fig.width=9, fig.height=4}
if (!is.null(params$availability_plot_cal)) print(params$availability_plot_cal)
```

## 2.3 Availability Frequency

Count of IDF units per daylight-availability category.

<!-- Source: plot_availability_frequency(), R/availability_daylight.R -->
```{r availability-freq, fig.width=6, fig.height=3}
if (!is.null(params$availability_plot_freq)) print(params$availability_plot_freq)
```

## 2.4 Spatial Distribution of Unavailability

Spatial distribution of unavailability, by turbine (point size/colour = % of the month's daylight monitoring period offline, for that turbine's primary IDF unit).

<!-- Source: turbine_availability_dt <- join_availability_to_turbine(); plot_availability_spatial(), both R/availability_daylight.R -->
```{r availability-spatial, fig.width=9, fig.height=7}
if (!is.null(params$availability_plot_spatial)) print(params$availability_plot_spatial)
```

# 3. Observed Species

## 3.1 Species Richness Summary

Number of tracks by count of distinct species classifications recorded within the same track, for tracks recorded in this month.

<!-- Source: monthly_richness_summary <- summarise_species_richness(monthly_richness_dt), R/id_transitions.R (monthly_richness_dt from track_species_summary()) -->
```{r richness-table}
if (!is.null(params$richness_dt)) report_table(params$richness_dt)
```

## 3.2 Species Richness Distribution

Same data as 3.1, as a histogram.

<!-- Source: plot_species_richness_hist(), R/id_transitions.R -->
```{r richness-plot, fig.width=6, fig.height=4}
if (!is.null(params$richness_plot)) print(params$richness_plot)
```

# 4. Curtailments by Species

## 4.1 Curtailments by Species

Curtailment events triggered in this month, one row per species.

<!-- Source: summarise_curtailment_species(), R/curtailment_species.R (built on classify_curtailment_species()) -->
```{r curtl-species-table}
if (!is.null(params$curtl_by_species_dt)) report_table(params$curtl_by_species_dt)
```

## 4.2 Curtailments by Species Group

Same events, rolled up by species group (priority / nonpriority / other / uncategorized).

<!-- Source: summarise_curtailment_species_group(), R/curtailment_species.R -->
```{r curtl-group-table}
if (!is.null(params$curtl_by_group_dt)) report_table(params$curtl_by_group_dt)
```

# 5. Short-Track Curtailments

Curtailments triggered by tracks with fewer than `r params$shorttrack_min_points` recorded points, considered only within `r params$shorttrack_eval_range_m` m of the turbine.

<!-- Source: summarise_short_track_curtailments(), R/curtailment_short_track.R (built on classify_short_track_curtailments()) -->
```{r short-track-table}
if (!is.null(params$short_track_summary_dt)) report_table(params$short_track_summary_dt)
```

# 6. Curtailment Response Assessment

Whether SCADA-recorded RPM dropped as expected in response to curtailment signals, for the turbines and window with SCADA coverage this month. The SCADA baseline immediately before/after each signal is trusted only within `r params$curtailment_start_end_gap_sec` s; an immediate response is recorded when RPM drops by at least `r params$curtailment_drop_pct_threshold * 100`% within `r params$curtailment_max_next_gap_sec` s of the signal; a turbine is considered stopped once RPM falls below `r params$safe_shutdown_rpm`.

## 6.1 By Status

<!-- Source: summary_assess$by_status <- summarise_curtailment_assessment(assess_dt)$by_status, R/curtailment_response.R (assess_dt from assess_curtailment_response()) -->
```{r assess-status-table}
if (!is.null(params$assess_by_status)) report_table(params$assess_by_status)
```

## 6.2 By Turbine

Same assessment, broken down by turbine.

<!-- Source: summary_assess$by_turbine <- summarise_curtailment_assessment(assess_dt)$by_turbine, R/curtailment_response.R -->
```{r assess-turbine-table}
if (!is.null(params$assess_by_turbine)) report_table(params$assess_by_turbine)
```

# 7. Shutdown Time

Time from curtailment signal to reaching each RPM threshold, by turbine. Bands below/above the agreed cut-offs are reported as-is, without further interpretation.

## 7.1 Time to Threshold by Turbine

<!-- Source: summarise_time_to_threshold(tt_dt), R/curtailment_shutdown_time.R (tt_dt from time_to_rpm_thresholds()) -->
```{r shutdown-turbine-table}
if (!is.null(params$shutdown_by_turbine)) report_table(params$shutdown_by_turbine)
```

<!--
7.1's table is wide (1 row per turbine, many columns) and does not fit a
portrait A4 page -- this section break makes JUST the page(s) up to this
point (i.e. 7.1's table) render landscape; everything from 7.2 onward
reverts to the document's default portrait page_size (set in the YAML
header above). Requires the officedown package (output format changed
from word_document to officedown::rdocx_document above) -- officer is
already a dependency via flextable, officedown adds the block_section()/
prop_section() Word section-break support that plain rmarkdown::word_document
does not have.
-->
```{r shutdown-turbine-landscape, echo=FALSE}
officer::block_section(
  officer::prop_section(
    page_size = officer::page_size(orient = "landscape", width = 11.69, height = 8.27),
    type = "continuous"
  )
)
```

## 7.2 Time to Threshold Bands

Same events, grouped into bands below/above the agreed cut-offs (`r params$shutdown_time_low_cut` s / `r params$shutdown_time_high_cut` s).

<!-- Source: summarise_time_to_threshold_bands(tt_dt), R/curtailment_shutdown_time.R -->
```{r shutdown-bands-table}
if (!is.null(params$shutdown_bands)) report_table(params$shutdown_bands)
```

## 7.3 Time to Threshold Distribution

<!-- Source: plot_time_to_threshold(), R/curtailment_shutdown_time.R -->
```{r shutdown-plot, fig.width=7, fig.height=6}
if (!is.null(params$shutdown_plot)) print(params$shutdown_plot)
```

# 8. Safe Distance (KNE Methodology)

Distance between the triggering track and the turbine at the moment of curtailment, compared against the KNE reference line (`r params$safe_dist_reference_line_m` m), by priority species. A turbine's estimated time-to-stop-safely uses `r params$safe_dist_rpm_threshold` rpm as the "stopped" threshold; a turbine already below `r params$safe_dist_already_slowing_rpm` rpm at the moment of the signal is treated as already slowing from a previous curtailment, not at full operating speed.

## 8.1 Overall

<!-- Source: summary_safe_dist$overall <- summarise_safe_distance(safe_dist_dt, prioritysp)$overall, R/curtailment_safe_distance.R (safe_dist_dt from compute_safe_distance()) -->
```{r safe-dist-overall-table}
if (!is.null(params$safe_dist_overall)) report_table(params$safe_dist_overall)
```

## 8.2 By Species

<!-- Source: summary_safe_dist$by_species <- summarise_safe_distance(safe_dist_dt, prioritysp)$by_species, R/curtailment_safe_distance.R -->
```{r safe-dist-species-table}
if (!is.null(params$safe_dist_by_species)) report_table(params$safe_dist_by_species)
```

## 8.3 Distribution

<!-- Source: plot_safe_distance_hist(), R/curtailment_safe_distance.R -->
```{r safe-dist-plot, fig.width=8, fig.height=8}
if (!is.null(params$safe_dist_plot)) print(params$safe_dist_plot)
```

# 9. Bi-Directional ID Transitions

Curtailments triggered by a species reclassification within the same track, in both directions (priority-to-nonpriority and nonpriority-to-priority) -- global, across all non-priority species together, not any single species. A reclassification is considered "late" when it happens more than `r params$id_transition_late_time_sec` s after the curtailment start, or when the track was already within `r params$track_proximity_threshold_m` m of the turbine at the moment of reclassification.

## 9.1 Risk by Direction

<!-- Source: monthly_id_risk_summary$by_direction <- summarise_id_transition_risk(monthly_id_risk_dt, curtl_dt)$by_direction, R/id_transitions.R (monthly_id_risk_dt from classify_id_transition_risk()) -->
```{r id-risk-table}
if (!is.null(params$id_risk_by_direction)) report_table(params$id_risk_by_direction)
```

<!--
9.2 e' opcional (run_sections_monthly$id_confusion, DESLIGADA por omissao
em monthlyReportSettings.R) -- analise pontual para UMA especie
(id_confusion_species_of_interest), nao uma metrica de rotina mensal.
Quando desligada, params$id_confusion_general fica NULL e todo o
subsection (titulo, texto e tabela) desaparece do documento -- nao so' a
tabela -- por isso o titulo/texto tambem estao dentro deste chunk
condicional (results='asis'), nao como markdown normal.
-->
```{r id-confusion-heading, results='asis'}
if (!is.null(params$id_confusion_general)) {
  cat(sprintf("## 9.2 Species Confusion (%s)\n\n", params$id_confusion_species))
  cat(sprintf(
    "Other species recorded within the same track as %s, all tracks (not only curtailment-triggering ones).\n\n",
    params$id_confusion_species
  ))
}
```

<!-- Source: monthly_id_confusion_summary$confusion_general <- summarise_species_confusion(), R/id_transitions.R -->
```{r id-confusion-table}
if (!is.null(params$id_confusion_general)) report_table(params$id_confusion_general)
```

# 10. Biological Flight Metrics

Flight speed and flight height per species, for tracks with at least `r params$flight_min_track_points` recorded points and a flight speed between `r params$flight_speed_ms_min` and `r params$flight_speed_ms_max` m/s. The shaded band in the height distribution (10.3) marks the `r params$riskHeight_lower`-`r params$riskHeight_upper` m risk zone.

## 10.1 Flight Speed by Species

<!-- Source: summarise_flight_speed(monthly_flight_base_dt), R/bio_flight_metrics.R (monthly_flight_base_dt from flight_metrics_base()) -->
```{r flight-speed-table}
if (!is.null(params$flight_speed_by_species)) report_table(params$flight_speed_by_species)
```

## 10.2 Flight Height by Species

<!-- Source: summarise_flight_height(monthly_flight_base_dt), R/bio_flight_metrics.R -->
```{r flight-height-table}
if (!is.null(params$flight_height_by_species)) report_table(params$flight_height_by_species)
```

## 10.3 Distribution

<!-- Source: plot_flight_metrics_distribution(), R/bio_flight_metrics.R -->
```{r flight-metrics-plot, fig.width=8, fig.height=6}
if (!is.null(params$flight_metrics_plot)) print(params$flight_metrics_plot)
```

# 11. Minimum Individuals per Time Bin

Minimum number of distinct individuals per priority species detected in the same `r params$min_individuals_bin_min`-minute time bin (2 tracks count as 1 individual when within `r params$min_individuals_merge_dist_m` m of each other), farm-wide, summarised by day.

## 11.1 Summary

<!-- Source: summarise_min_individuals(monthly_min_indiv_bins_dt), R/track_min_individuals.R (monthly_min_indiv_bins_dt from count_min_individuals_per_bin()) -->
```{r min-indiv-summary-table}
if (!is.null(params$min_indiv_summary)) report_table(params$min_indiv_summary)
```

## 11.2 Daily Peak, by Species

<!-- Source: plot_daily_max_individuals(monthly_min_indiv_daily_dt, species_sel = prioritysp), R/track_min_individuals.R (monthly_min_indiv_daily_dt from summarise_daily_max_individuals()) -->
```{r min-indiv-daily-plot, fig.width=8, fig.height=6}
if (!is.null(params$min_indiv_daily_plot)) print(params$min_indiv_daily_plot)
```

# Annexes

The full detail behind each table above (including all rows, not only the summaries shown here) is provided as separate files in the same output folder as this report, one workbook/plot set per section: data summary, system availability (including the turbine-level spatial availability table), observed species, curtailments by species, short-track curtailments, curtailment response assessment, shutdown time, safe distance, ID transitions and species confusion, biological flight metrics, and minimum individuals per bin.
