---
title: "`r params$title`"
output: word_document
params:
  title: ""
  project_ref: ""
  report_month: ""
  report_start: ""
  report_end: ""
  analysis_date: ""
  username: ""
  code_version: ""

  techsum_daylight_mins_total: !r NULL
  techsum_offline_mins_total: !r NULL
  techsum_offline_pct: !r NULL
  techsum_curtl_priority_n: !r NULL
  techsum_curtl_priority_pct: !r NULL
  techsum_curtl_nonpriority_n: !r NULL
  techsum_curtl_nonpriority_pct: !r NULL
  techsum_latency_mean_sec: !r NULL
  techsum_no_response_n: !r NULL
  techsum_no_response_pct: !r NULL
  techsum_shutdown_mean_sec: !r NULL
  techsum_shutdown_max_sec: !r NULL
  techsum_unnecessary_n: !r NULL
  techsum_unnecessary_pct: !r NULL

  data_summary: !r NULL
  coverage_summary: !r NULL
  coverage_plot: !r NULL
  coverage_considered_turbines_text: !r NULL
  coverage_incomplete_turbines_text: !r NULL

  availability_by_idf: !r NULL
  availability_plot_cal: !r NULL
  availability_plot_freq: !r NULL
  availability_plot_spatial: !r NULL

  offline_evidence_by_idf: !r NULL
  offline_evidence_overall: !r NULL
  offline_evidence_scope_note: !r NULL
  net_availability_overall: !r NULL

  richness_dt: !r NULL
  entropy_plot: !r NULL

  curtl_by_species_dt: !r NULL
  curtl_by_group_dt: !r NULL

  short_track_summary_dt: !r NULL

  latency_by_turbine: !r NULL
  latency_bands: !r NULL
  latency_plot: !r NULL
  latency_timeline_plot: !r NULL
  latency_n_no_data: !r NULL
  latency_pct_no_data: !r NULL
  latency_n_below_cutin: !r NULL
  latency_pct_below_cutin: !r NULL

  no_response_examples_plot: !r NULL
  slowest_response_examples_plot: !r NULL
  n_no_response_examples: !r NULL
  n_slowest_examples: !r NULL
  xlsx_curtailment_examples: !r NULL

  shutdown_by_turbine: !r NULL
  shutdown_bands: !r NULL
  shutdown_plot: !r NULL

  safe_dist_overall: !r NULL
  safe_dist_by_species: !r NULL
  safe_dist_plot: !r NULL
  safe_dist_plot_height_in: 3.94

  id_risk_by_direction: !r NULL
  id_confusion_species: !r NULL
  id_confusion_general: !r NULL

  flight_speed_by_species: !r NULL
  flight_height_by_species: !r NULL
  flight_metrics_plot: !r NULL

  min_indiv_summary: !r NULL
  min_indiv_daily_plot: !r NULL

  # Literais de configuracao (monthlyReportSettings_BSH.R/_DGY.R) usados so' para
  # texto descritivo -- cada secção que aplica um threshold/cut-off mostra
  # o VALOR concreto usado nesse mes, nao so' o nome do parametro.
  heartbeat_interval_min: !r NULL
  heartbeat_offline_gap_min: !r NULL
  idf_availability_top_n: !r NULL
  availability_cal_body_top_n: !r NULL
  availability_cal_extended_filename: !r NULL

  shorttrack_min_points: !r NULL
  shorttrack_eval_range_m: !r NULL

  curtailment_start_end_gap_sec: !r NULL
  curtailment_max_next_gap_sec: !r NULL
  curtailment_drop_pct_threshold: !r NULL
  safe_shutdown_rpm: !r NULL
  turbinas_scada_used: !r NULL

  shutdown_time_thresholds: !r NULL
  shutdown_time_low_cut: !r NULL
  shutdown_time_high_cut: !r NULL
  shutdown_time_buffer_sec: !r NULL

  curtailment_latency_decline_pct: !r NULL
  curtailment_cutin_rpm: !r NULL
  response_timeline_unit: !r NULL

  curtailment_example_window_before_min: !r NULL
  curtailment_example_window_after_min: !r NULL

  safe_dist_reference_line_m: !r NULL
  safe_dist_rpm_threshold: !r NULL
  safe_dist_already_slowing_rpm: !r NULL

  id_transition_late_time_sec: !r NULL
  track_proximity_threshold_m: !r NULL

  flight_min_track_points: !r NULL
  flight_speed_ms_min: !r NULL
  flight_speed_ms_max: !r NULL
  riskHeight_lower: !r NULL
  riskHeight_upper: !r NULL

  min_individuals_bin_min: !r NULL
  min_individuals_merge_dist_m: !r NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Tabela flextable com o estilo visual do relatorio. max_col_width_cm (opcional)
# limita CADA coluna a esse maximo (cm) -- nao forca todas as colunas a esse
# tamanho, so' encolhe as que o autofit() deixaria mais largas (ver
# cap_col_width() abaixo). Usado nas secções 6.2 e 7.1 (tabelas largas, 1
# linha por turbina), pedido explicito para caberem numa pagina A4 vertical.
# round_display() (ver abaixo) corre sempre primeiro, aqui dentro -- nenhuma
# tabela do relatorio precisa de a chamar manualmente.
report_table <- function(x, caption = NULL, max_col_width_cm = NULL, col_widths_cm = NULL) {
  ft <- flextable::flextable(round_display(x)) |>
    flextable::theme_box() |>
    flextable::bg(part = "header", bg = "gray85") |>
    flextable::bold(part = "header") |>
    flextable::fontsize(size = 9, part = "header") |>
    flextable::fontsize(size = 9, part = "body") |>
    flextable::align(align = "center", part = "header") |>
    flextable::valign(valign = "center", part = "all") |>
    flextable::autofit()
  if (!is.null(max_col_width_cm)) ft <- cap_col_width(ft, max_col_width_cm)
  if (!is.null(col_widths_cm)) ft <- set_col_max_width(ft, col_widths_cm)
  if (!is.null(caption)) ft <- flextable::set_caption(ft, caption)
  ft
}

# Arredonda, so' para apresentacao no docx, cada coluna numerica que tenha
# algum valor nao-inteiro para `digits` casas decimais (2 por omissao) --
# colunas so' com valores inteiros (contagens) ficam como estao. Excecao: se
# arredondar a `digits` casas desse 0 mas o valor real nao e' zero, estende
# casas decimais ate aparecer o 1o digito significativo (ex: 0.001), para
# nao mostrar "0.00" nalgo que na realidade nao e' zero. Devolve os valores
# ja como texto formatado (sprintf) -- o formatador automatico do flextable
# nao garante um numero fixo de casas decimais (mostraria "12.3", nao
# "12.30"). So' afeta o que aparece no docx: os exports xlsx (feitos a
# partir dos objetos originais, nao deste helper) mantêm sempre os valores
# tal como calculados pelas funcoes de analise.
round_display <- function(x, digits = 2) {
  x <- as.data.frame(x)
  for (col in names(x)) {
    v <- x[[col]]
    if (!is.numeric(v) || is.integer(v)) next
    if (all(v == round(v), na.rm = TRUE)) next
    x[[col]] <- vapply(v, function(val) {
      if (is.na(val)) return(NA_character_)
      d <- digits
      while (round(val, d) == 0 && val != 0 && d < 6) d <- d + 1
      sprintf(paste0("%.", d, "f"), val)
    }, character(1))
  }
  x
}

cap_col_width <- function(ft, max_width_cm = 2) {
  # dim() (nao flextable::dim()) -- dim.flextable e' um metodo S3 registado
  # pelo flextable no generico base dim(), nao necessariamente exportado como
  # simbolo chamavel via flextable::dim()
  widths_in <- dim(ft)$widths
  capped_cm <- pmin(widths_in * 2.54, max_width_cm)
  flextable::width(ft, j = seq_along(capped_cm), width = capped_cm, unit = "cm")
}

# Como cap_col_width(), mas por coluna -- widths_cm e' um vector nomeado
# c("Nome da Coluna" = largura_maxima_cm, ...), usando os nomes ja'
# apresentados (apos rename_display()). So' encolhe (nunca alarga) as
# colunas indicadas ate' esse maximo; colunas nao mencionadas ficam como o
# autofit() as deixou. Nomes que nao existirem na tabela sao ignorados.
set_col_max_width <- function(ft, widths_cm) {
  widths_in <- dim(ft)$widths
  idx <- match(names(widths_cm), ft$col_keys)
  hit <- !is.na(idx)
  if (any(hit)) {
    capped_cm <- pmin(widths_in[idx[hit]] * 2.54, unname(widths_cm[hit]))
    ft <- flextable::width(ft, j = idx[hit], width = capped_cm, unit = "cm")
  }
  ft
}

# Renomeia colunas so' para APRESENTACAO no docx -- os exports em xlsx
# (annexos) usam sempre os nomes tecnicos originais dos objetos R. mapping:
# c(nome_original = "Nome Legivel"); colunas nao mencionadas ficam como estao.
rename_display <- function(x, mapping) {
  x <- as.data.frame(x)
  idx <- match(names(mapping), names(x))
  hit <- !is.na(idx)
  names(x)[idx[hit]] <- unname(mapping)[hit]
  x
}

# Remove colunas da tabela apresentada no docx (o xlsx correspondente, feito
# a partir do objeto original nao filtrado, continua completo)
drop_cols <- function(x, cols) {
  x <- as.data.frame(x)
  x[, setdiff(names(x), cols), drop = FALSE]
}

# Substitui VALORES (nao nomes de coluna) de uma coluna categorica por
# rotulos legiveis -- usado para as categorias de risk_direction (9.1)
recode_values <- function(x, col, mapping) {
  x <- as.data.frame(x)
  hit <- x[[col]] %in% names(mapping)
  x[[col]][hit] <- unname(mapping[x[[col]][hit]])
  x
}
```

<!--
Cada tabela/plot abaixo tem, imediatamente acima do chunk que a produz, um
comentario "Source: ..." a apontar para a funcao R (e ficheiro) que calcula
o objeto correspondente em IDF_monthly_report.R -- usar isso para encontrar
rapidamente onde ajustar cada tabela/plot (colunas, arredondamento, filtros,
etc.) sem ter de procurar pelo nome do param em todo o script. Estes
comentarios HTML nao aparecem no .docx gerado.

Cada tabela/plot tem tambem a sua propria subsecção (##), com 1 frase a
identificar o objeto, mesmo quando 2 tabelas pertencem à mesma secção -- 2
flextables em chunks consecutivos sem nenhum paragrafo de texto a
separa-los tendem a sair "coladas" no docx (dificeis de selecionar/mover/
editar independentemente no Word). Uma frase de texto entre elas garante
uma quebra de paragrafo real a separa-las.

Documento TODO em A4 vertical -- uma tentativa anterior de tornar so' a
secção 7.1 landscape (via officedown::block_section) saiu com um bug: sem
UM SEGUNDO section break antes de 7.1, o primeiro break aplicava-se a TODO
o conteudo anterior (secções 1-6.2 saiam landscape tambem, nao so' 7.1).
Solucao adotada: manter tudo vertical e caber as tabelas largas (6.2, 7.1)
por colunas mais estreitas (max_col_width_cm) e nomes de coluna mais curtos,
em vez de mexer na orientacao da pagina.
-->

**`r params$project_ref`**

Monthly report: `r params$report_month`

Report period: `r params$report_start` to `r params$report_end`

Analysis date: `r params$analysis_date`

Responsible: `r params$username`

Code version: `r params$code_version`

This report is descriptive and fully automated, generated end-to-end by an R code pipeline. It presents the metrics produced by the IDF analysis pipeline for the month above, without further interpretation, except where an explicit threshold (e.g. the KNE safe-distance reference line, shutdown-time bands) is already part of the pre-defined methodology.

---

<!--
Technical Summary -- secção pedida pelo Paulo (2026-09) SEM numeração, por
isso texto em negrito (**...**), nao um heading (#/##) -- este documento so'
tem numeracao automatica de secções porque o reference_docx usado
(rmarkdown::render(), R/report.R) liga os estilos "Heading 1"/"Heading 2" a
uma lista numerada do Word; texto em negrito normal fica fora dessa lista,
tal como o bloco de metadados acima. Cada frase e' omitida (nao "NA"/vazia)
se a secção de origem estivesse desligada ou sem dados este mes -- ver os
techsum_* == NULL abaixo, IDF_monthly_report.R secção 9 e
R/monthly_technical_summary.R. As referencias "secção N.M" abaixo apontam
para os headings numerados mais a frente neste mesmo documento -- se a
ordem/contagem de secções acima mudar, conferir que ainda batem certo.
-->
```{r technical-summary, results='asis'}
cat("**Technical Summary**\n\n")

if (!is.null(params$techsum_daylight_mins_total)) {
  techsum_availability_txt <- sprintf(
    "- **Overall IDF Availability**: this month, the farm's IDF units had %s total minutes of daylight monitoring time, of which %s minutes (%.1f%%) were offline on a raw, heartbeat-only basis (see System Availability, section 2). Offline time only starts counting once a heartbeat gap exceeds %s minutes (at least 2 consecutive heartbeats missed), and even then the first %s minutes of that gap are still counted as online -- a single missed heartbeat, on its own, never registers as offline time.",
    format(round(params$techsum_daylight_mins_total), big.mark = ","),
    format(round(params$techsum_offline_mins_total), big.mark = ","),
    params$techsum_offline_pct,
    params$heartbeat_offline_gap_min,
    params$heartbeat_interval_min
  )
  if (!is.null(params$net_availability_overall)) {
    techsum_availability_txt <- paste0(techsum_availability_txt, sprintf(
      " Once minutes with confirmed evidence of continued operation are excluded (a curtailment fired despite the missing heartbeat), net offline time drops to %.1f%% -- see the Unavailability Summary in section 2.3 for the full raw/net/pending-review breakdown, since this distinction matters for contract-availability reporting.",
      params$net_availability_overall$net_offline_pct
    ))
  }
  cat(paste0(techsum_availability_txt, "\n"))
}

if (!is.null(params$techsum_curtl_priority_n)) {
  cat(sprintf(
    "- **Curtailments**: of the curtailment events triggered this month, %.0f (%.1f%%) were triggered by priority species and %.0f (%.1f%%) by non-priority species (see Curtailments by Priority Group, section 4.2).\n",
    params$techsum_curtl_priority_n, params$techsum_curtl_priority_pct,
    params$techsum_curtl_nonpriority_n, params$techsum_curtl_nonpriority_pct
  ))
}

if (!is.null(params$techsum_latency_mean_sec)) {
  cat(sprintf(
    "- **Response Latency**: response latency is the time from the curtailment signal to the first SCADA-recorded RPM decline of at least %s%%; the overall mean this month was %.1f s (see Response Latency, section 6.1).\n",
    params$curtailment_latency_decline_pct * 100, params$techsum_latency_mean_sec
  ))
}

if (!is.null(params$techsum_shutdown_mean_sec)) {
  cat(sprintf(
    "- **Shutdown Time**: shutdown time is the time from the curtailment signal to the turbine's RPM falling below %s (the \"stopped\" threshold); the overall mean this month was %.1f s, with the longest recorded shutdown taking %.1f s (see Shutdown Time, section 6.2).\n",
    params$safe_shutdown_rpm, params$techsum_shutdown_mean_sec, params$techsum_shutdown_max_sec
  ))
}

if (!is.null(params$techsum_no_response_n)) {
  cat(sprintf(
    "- **No-Response / Missed Curtailments**: %.0f curtailment(s) (%.1f%% of those evaluated) showed no detected response this month (see No-Response Events, section 6.3).\n",
    params$techsum_no_response_n, params$techsum_no_response_pct
  ))
}

if (!is.null(params$techsum_unnecessary_n)) {
  cat(sprintf(
    "- **Unnecessary Curtailments**: a P to NP (unnecessary curtailment) is a curtailment triggered while classified as a priority species, but the track's final classification was non-priority -- section 8.1 (Risk by Direction) counts the tracks in this category; counting instead the individual curtailment events they triggered (a single track can trigger more than one), %.0f curtailment(s) (%.1f%% of all curtailments this month) fall in this category.\n",
    params$techsum_unnecessary_n, params$techsum_unnecessary_pct
  ))
}
```

---

# Data Universe and Time Span

## Row Counts and Date Range

Row counts and date range of each dataset used in this report, restricted to the month above (SCADA row count restricted to the SCADA-availability window intersected with the month).

<!-- Source: monthly_data_summary_dt <- summarise_dataset_extent(), R/dataset_summary.R (called from IDF_monthly_report.R, section "0. Data extent / quantities table") -->
```{r data-summary-table}
if (!is.null(params$data_summary)) {
  report_table(rename_display(
    params$data_summary,
    c(dataset = "Dataset", n_rows = "Rows", date_from = "From", date_to = "To", n_days = "Days")
  ))
}
```

## Temporal Coverage

Day-by-day data presence for each dataset within the month -- complements 1.1, which only gives the overall min/max/row count and does not show whether there are gaps within that range.

Turbines with data on both curtailments and SCADA this month, considered for further analysis (turbines with data on only one side, or neither, are omitted here -- otherwise most of the farm would show up with 0%/undefined overlap, since only a subset of turbines has SCADA installed): `r params$coverage_considered_turbines_text`. Of these, turbines with incomplete overlap (days with one but not the other): `r params$coverage_incomplete_turbines_text`. The full day-by-day breakdown per turbine, including turbines outside the considered set, is in the accompanying workbook and plot (data_coverage_turbine_overlap\_*.xlsx/.png), not reproduced here.

<!-- Source: monthly_coverage_summary_dt <- data_coverage_summary(); p_monthly_coverage <- plot_data_coverage(monthly_coverage_calendar_dt <- data_coverage_calendar()), all R/data_coverage.R. Turbine-level overlap (coverage_considered_turbines_text/coverage_incomplete_turbines_text): monthly_coverage_overlap_summary_dt <- overlap_summary_by_turbine(daily_overlap_by_turbine()), same file, filtered to days_a>0 & days_b>0 -- annex has the unfiltered version (plot_daily_overlap_by_turbine(), too tall to embed with turbinas_scada="all") -->
```{r coverage-summary-table}
if (!is.null(params$coverage_summary)) {
  report_table(
    rename_display(
      params$coverage_summary,
      c(dataset = "Dataset", start = "From", end = "To", total_days = "Total Days",
        days_with_data = "Days with Data", days_missing = "Days Missing", pct_missing = "% Missing")
    ),
    col_widths_cm = c(
      "Total Days" = 1.5, "Days with Data" = 1.5, "Days Missing" = 1.5, "% Missing" = 1.5
    )
  )
}
```

```{r coverage-plot, fig.width=7, fig.height=4}
if (!is.null(params$coverage_plot)) print(params$coverage_plot)
```

# System Availability (Heartbeats)

Heartbeats are expected every `r params$heartbeat_interval_min` minutes; an IDF unit is considered offline once the gap since its last heartbeat exceeds `r params$heartbeat_offline_gap_min` minutes (at least 2 consecutive heartbeats missed). Even then, the first `r params$heartbeat_interval_min` minutes of that gap are still counted as online, not offline -- a single missed heartbeat, on its own, never registers as offline time.

## Availability by IDF Unit

```{r availability-text, results='asis'}
if (!is.null(params$availability_by_idf) && nrow(params$availability_by_idf) > 0) {
  cat(sprintf(
    "This month covered %d day(s) of monitoring, %s total minutes of daylight monitoring time per IDF unit (same calendar for every unit, so not repeated per row below). The table below lists, per IDF unit, the percentage of that monitoring time it was offline, and an availability category grouping the corresponding availability percentage (100%% minus offline%%) into bands: <60%%, 60-80%%, 80-90%%, 90-96%%, and >96%%.\n\n",
    params$availability_by_idf$days_covered[1],
    format(params$availability_by_idf$daylight_mins_total[1], big.mark = ",")
  ))
}
```

<!-- Source: idf_availability_summary$by_idf <- summarise_availability(idf_availability_dt), R/availability_daylight.R (idf_availability_dt itself from daylight_availability()) -->
```{r availability-table}
if (!is.null(params$availability_by_idf)) {
  report_table(rename_display(
    drop_cols(params$availability_by_idf, c("daylight_mins_total", "days_covered", "offline_mins_total", "availability_pct")),
    c(idf = "IDF Unit", monitoring_period_pct = "Offline (%)", availability_cat = "Category")
  ))
}
```

## Availability Calendar

Every daylight time slot this month, laid out as a calendar (date on the horizontal axis, time of day on the vertical axis) -- restricted to the top `r params$availability_cal_body_top_n` units by offline time, so that each panel's time-of-day axis stays legible. The table in 2.1 above has every IDF unit. A slot without a heartbeat is classified by the evidence available for that period, rather than shown only as a percentage: whether a curtailment was triggered by the turbine(s) associated with that IDF unit during the gap, whether SCADA still recorded RPM readings from those turbines, both, or neither. Night-time slots are shown separately, since bird protection is only evaluated during daylight hours.

Each slot is colored by one of six statuses:

- **Online**: a heartbeat was received for this slot.
- **IDF unit communication failure**: no heartbeat, but a curtailment was triggered by the associated turbine(s) during the gap -- the unit was actively deciding/acting, so the missing heartbeat reflects a communication fault rather than bird protection being off.
- **Turbine operational, no detection**: no heartbeat and no curtailment, but SCADA still recorded RPM readings from the turbine(s) -- mechanically operational, simply with no bird triggering a response.
- **No evidence (heartbeat and SCADA both missing)**: neither signal is available for this slot; requires manual review, since it can reflect a genuine gap in bird-protection coverage or a data gap affecting heartbeat and SCADA at the same time.
- **Night**: outside daylight hours, when bird protection is not evaluated.
- **No data**: no underlying calendar data available for this slot, independent of the evidence check above.

<!-- Source: offline_evidence_slot_grid()/plot_offline_evidence_slots(), R/availability_daylight.R; classification from classify_offline_evidence(), R/offline_curtailment_check.R -->
```{r availability-cal, fig.width=6.30, fig.height=6.30}
if (!is.null(params$availability_plot_cal)) print(params$availability_plot_cal)
```
```{r availability-cal-annex, results='asis'}
if (!is.null(params$availability_cal_extended_filename)) {
  cat(sprintf("\n*An extended calendar (the top %s units by offline time) is available as an accompanying image: `%s`.*\n", params$idf_availability_top_n, params$availability_cal_extended_filename))
}
```

## Offline Evidence

Breakdown of every offline interval (a gap between heartbeats of at least `r params$heartbeat_offline_gap_min` minutes) by the evidence available for that period, this month -- see the Availability Calendar above for the same classification laid out over time. "IDF unit communication failure" means a curtailment was triggered during the gap (the unit was actively deciding/acting; a missing heartbeat is then attributable to a communication fault, not to bird protection being off). "Turbine operational, no detection" means no curtailment was triggered, but SCADA still recorded RPM readings from the turbine(s) (mechanically operational, simply with no bird triggering a response). "No evidence" means neither signal is available and requires manual review -- it can reflect a genuine gap in bird-protection coverage, or a data gap that happens to affect heartbeat and SCADA at the same time.

### Unavailability Summary

Three related but distinct numbers are relevant when assessing IDF unavailability, since they answer different questions and carry different implications where unavailability has contract consequences:

- **Raw offline**: any heartbeat gap of at least `r params$heartbeat_offline_gap_min` minutes, regardless of what else was observed during it -- the number a contract that defines availability strictly by heartbeat presence would measure against.
- **Net / confirmed offline**: the raw offline percentage minus the minutes classified as "IDF unit communication failure" in the breakdown below -- gaps during which a curtailment was actually triggered, proving the detection/decision system was operating even though the heartbeat itself failed to report it. Excluding this time avoids penalizing the system for a communication fault it did not actually have.
- **No evidence, pending manual review**: the share of monitoring time for which neither a curtailment nor a SCADA RPM reading was recorded during the gap -- the genuinely ambiguous case. This is already included within the net offline percentage above, not an additional deduction from it; it is shown separately because it requires manual, case-by-case review rather than being resolved automatically in either direction.

```{r net-availability-table}
if (!is.null(params$net_availability_overall)) {
  x <- params$net_availability_overall
  report_table(data.frame(
    Metric = c("Raw offline", "Net / confirmed offline", "No evidence (pending review; included in net offline above)"),
    `Minutes` = c(x$raw_offline_mins, x$net_offline_mins, x$no_evidence_mins),
    `% of Daylight Monitoring Time` = c(x$raw_offline_pct, x$net_offline_pct, x$no_evidence_pct),
    check.names = FALSE
  ))
}
```

```{r offline-evidence-heading-overall, results='asis'}
if (!is.null(params$offline_evidence_overall) && nrow(params$offline_evidence_overall) > 0) cat("\n\n**Farm-wide**\n")
```

<!-- Source: summarise_offline_evidence()$overall, R/offline_curtailment_check.R -->
```{r offline-evidence-table-overall}
if (!is.null(params$offline_evidence_overall) && nrow(params$offline_evidence_overall) > 0) {
  report_table(rename_display(
    params$offline_evidence_overall,
    c(classification = "Classification", n_intervals = "N Intervals", total_mins = "Total (min)", pct_of_total = "% of Total")
  ))
}
```

```{r offline-evidence-heading-by-idf, results='asis'}
if (!is.null(params$offline_evidence_by_idf) && nrow(params$offline_evidence_by_idf) > 0) cat("\n\n**By IDF Unit**\n")
```

<!-- Source: summarise_offline_evidence()$by_idf, R/offline_curtailment_check.R -->
```{r offline-evidence-table-by-idf}
if (!is.null(params$offline_evidence_by_idf) && nrow(params$offline_evidence_by_idf) > 0) {
  report_table(
    rename_display(
      params$offline_evidence_by_idf,
      c(idf = "IDF Unit", classification = "Classification", n_intervals = "N Intervals", total_mins = "Total (min)")
    ),
    max_col_width_cm = 4
  )
}
```

```{r offline-evidence-scope-note, results='asis'}
if (!is.null(params$offline_evidence_scope_note)) cat(sprintf("\n*%s*\n", params$offline_evidence_scope_note))
```

## Availability Frequency

Count of IDF units per daylight-availability category. Daylight availability is 100% minus the percentage of an IDF unit's daylight monitoring time it was offline this month (see Availability by IDF Unit, section 2.1, for the offline-time methodology and the category bands).

<!-- Source: plot_availability_frequency(), R/availability_daylight.R -->
```{r availability-freq, fig.width=6, fig.height=3}
if (!is.null(params$availability_plot_freq)) print(params$availability_plot_freq)
```

## Spatial Distribution of Unavailability

Spatial distribution of unavailability, by turbine (point size = % of the month's daylight monitoring period offline, for that turbine's primary IDF unit). Daylight availability (100% minus this offline percentage) follows the same monthly heartbeat-based methodology described in Availability by IDF Unit (section 2.1).

<!-- Source: turbine_availability_dt <- join_availability_to_turbine(); plot_availability_spatial(), both R/availability_daylight.R -->
```{r availability-spatial, fig.width=6.30, fig.height=4.72}
if (!is.null(params$availability_plot_spatial)) print(params$availability_plot_spatial)
```

# Observed Species

## Track Level Entropy

Normalised Shannon entropy (Pielou's evenness) of the sequence of species classifications recorded within each track, for tracks recorded this month. 0% = a track classified as a single species throughout (stable); 100% = classifications alternated as evenly as possible between the distinct species detected in that track (that track's own worst case). Being normalised by each track's own theoretical maximum, this is comparable across tracks with different numbers of distinct species, unlike the raw entropy value.

<!-- Source: plot_entropy_hist(monthly_richness_dt), R/id_transitions.R (monthly_richness_dt from track_species_summary(), shannon_evenness_pct computed there) -->
```{r entropy-plot, fig.width=6.30, fig.height=3.94}
if (!is.null(params$entropy_plot)) print(params$entropy_plot)
```

Number of tracks by count of distinct species classifications recorded within the same track, with the most frequent exact species combination for each count. For n_species = 1 there is no actual combination -- "Most Common Combination" there is simply the single most frequently detected species among tracks with only one classification.

<!-- Source: monthly_richness_summary <- summarise_species_richness(monthly_richness_dt), R/id_transitions.R (monthly_richness_dt from track_species_summary()) -- most_common_combo/most_common_combo_n added at source -->
```{r richness-table}
if (!is.null(params$richness_dt)) {
  report_table(
    rename_display(
      params$richness_dt,
      c(n_species = "N Species", n_tracks = "Tracks", pct = "%",
        most_common_combo = "Most Common Combination", most_common_combo_n = "Tracks with Combination")
    ),
    col_widths_cm = c("Most Common Combination" = 5, "Tracks with Combination" = 3)
  )
}
```

<!-- 3.2 (richness histogram) removida do docx por pedido -- a figura
continua a ser calculada e gravada em outputs/ (ver IDF_monthly_report.R,
secção 2), so' deixou de ser incluida no relatorio -->

# Curtailments by Species

## Curtailments by Species

Curtailment events triggered in this month, one row per species -- ordered by group (priority, then non-priority, then other/uncategorized), and by % of total within each group.

<!-- Source: summarise_curtailment_species(), R/curtailment_species.R (built on classify_curtailment_species()) -- row order fixed at source, see group_order in summarise_curtailment_species() -->
```{r curtl-species-table}
if (!is.null(params$curtl_by_species_dt)) {
  report_table(rename_display(
    params$curtl_by_species_dt,
    c(species_group = "Group", species = "Species", n = "N", pct_of_group = "% of Group", pct_of_total = "% of Total")
  ))
}
```

## Curtailments by Priority Group

Same events, rolled up by species group (priority / nonpriority / other / uncategorized).

<!-- Source: summarise_curtailment_species_group(), R/curtailment_species.R -->
```{r curtl-group-table}
if (!is.null(params$curtl_by_group_dt)) {
  report_table(rename_display(
    params$curtl_by_group_dt,
    c(species_group = "Group", n = "N", pct_of_total = "% of Total")
  ))
}
```

# Short-Track Curtailments

Curtailments triggered by tracks with fewer than `r params$shorttrack_min_points` recorded points, considered only within `r params$shorttrack_eval_range_m` m of the turbine.

<!-- Source: summarise_short_track_curtailments(), R/curtailment_short_track.R (built on classify_short_track_curtailments()) -->
```{r short-track-table}
if (!is.null(params$short_track_summary_dt)) report_table(params$short_track_summary_dt)
```

# Curtailment Response & Latency

Whether SCADA-recorded RPM dropped as expected in response to curtailment signals, for the turbines and window with SCADA coverage this month (`r params$turbinas_scada_used` -- all turbines with SCADA data in this window, per turbinas_scada = "all" in the monthly settings). The SCADA baseline used for each curtailment is the last RPM reading recorded at or before the signal, within `r params$curtailment_start_end_gap_sec` s of it; a reading recorded after the signal is never used for this purpose, so that the baseline cannot itself include any part of the response it is meant to measure. `r params$latency_n_no_data` curtailments (`r params$latency_pct_no_data`% of the total) have no such reading within that tolerance and are excluded from every table below, since no baseline RPM could be established for them; this reflects gaps in SCADA-RPM data availability, which vary by turbine and period (see the Response Latency by Turbine table below, and the accompanying workbook, curtailment_response_latency_*.xlsx, for the no-data share by turbine). A response is considered to have started once RPM has dropped by at least `r params$curtailment_latency_decline_pct * 100`% from its value at the start of the curtailment order; a turbine is considered stopped once RPM falls below `r params$safe_shutdown_rpm`. Both response latency and shutdown time below allow up to `r params$shutdown_time_buffer_sec` s past the end of the curtailment order for this to happen. Curtailments with an RPM below `r params$curtailment_cutin_rpm` (the cut-in speed, below which the turbine is not producing energy) at the start of the order are further excluded from the Response Latency and No-Response Events tables below, since there is no meaningful response to measure on a turbine that was already not operating: of the curtailments with a valid SCADA baseline this month, `r params$latency_n_below_cutin` (`r params$latency_pct_below_cutin`%) fall in this category.

## Response Latency

Time from the curtailment signal to the first SCADA reading showing the decline defined above, by turbine, among curtailments at or above the cut-in speed. Having SCADA data this month (the list above) is necessary but not sufficient to appear below -- a turbine also needs at least one curtailment whose SCADA baseline falls within the matching tolerance stated above, which in a given month only a subset of turbines actually achieves; turbines with no valid SCADA match this month are omitted here. The complete table, with every turbine, is in the accompanying workbook (curtailment_response_latency\_*.xlsx).

<!-- Source: summarise_latency_by_turbine(latency_dt), R/curtailment_response_latency.R -->
```{r latency-turbine-table}
if (!is.null(params$latency_by_turbine)) {
  report_table(
    rename_display(
      drop_cols(params$latency_by_turbine, c(
        "n_curtailments", "n_no_data", "pct_no_data", "n_known",
        "n_below_cutin", "pct_below_cutin", "n_no_response", "pct_no_response"
      )),
      c(
        turbine = "Turbine", n_eligible = "Curtailments", n_reached = "Reached",
        pct_reached = "% Reached", mean_latency_sec = "Mean (s)", median_latency_sec = "Median (s)"
      )
    ),
    max_col_width_cm = 2
  )
}
```

### Response Latency Bands

Of the curtailments where a decline was detected, share with latency within each cut-off.

<!-- Source: summarise_latency_bands(latency_dt), R/curtailment_response_latency.R -->
```{r latency-bands-table}
if (!is.null(params$latency_bands)) {
  report_table(rename_display(
    params$latency_bands,
    c(cutoff_sec = "Cut-off (s)", pct_within_cutoff = "% Within Cut-off")
  ))
}
```

### Response Latency Distribution

<!-- Source: plot_latency_histogram(latency_dt), R/curtailment_response_latency.R -->
```{r latency-plot, fig.width=7, fig.height=4}
if (!is.null(params$latency_plot)) print(params$latency_plot)
```

### Latency Temporal Pattern

Mean and standard deviation of response latency, among curtailments at or above the cut-in speed, aggregated by `r params$response_timeline_unit`.

<!-- Source: plot_latency_timeline(summarise_latency_timeline(latency_dt, unit = response_timeline_unit)), R/curtailment_response_timeline.R -->
```{r latency-timeline-plot, fig.width=7, fig.height=4.5}
if (!is.null(params$latency_timeline_plot)) print(params$latency_timeline_plot)
```

## Shutdown Time

Time from curtailment signal to reaching each RPM threshold, by turbine -- 3 thresholds evaluated: `r paste(params$shutdown_time_thresholds, collapse = ", ")` rpm. Bands below/above the agreed cut-offs are reported as-is, without further interpretation. Uses the same population as Response Latency above: curtailments with no SCADA baseline within `r params$curtailment_start_end_gap_sec` s of the signal, or already below the cut-in speed at the start of the order, are excluded (see the counts stated there).

### Time to Threshold by Turbine

<!-- Source: summarise_time_to_threshold(tt_dt), R/curtailment_shutdown_time.R (tt_dt from time_to_rpm_thresholds()) -->
```{r shutdown-turbine-table}
if (!is.null(params$shutdown_by_turbine)) {
  report_table(
    rename_display(
      drop_cols(params$shutdown_by_turbine, c("median_time_sec")),
      c(
        turbine = "Turbine", threshold = "Thresh. (rpm)", n_curtailments = "Curtailments",
        n_reached = "Reached", pct_reached = "% Reached", mean_time_sec = "Mean (s)",
        sd_time_sec = "SD (s)", min_time_sec = "Min (s)",
        max_time_sec = "Max (s)"
      )
    ),
    max_col_width_cm = 2
  )
}
```

### Time to Threshold Bands

Same events, grouped by threshold (ascending, lowest rpm reached first) into bands below/above the agreed cut-offs. A curtailment counts as "below cut" when it reached the threshold in under `r params$shutdown_time_low_cut` s (fast), and "above cut" when it took more than `r params$shutdown_time_high_cut` s (slow); cases in between count towards neither band.

<!-- Source: summarise_time_to_threshold_bands(tt_dt), R/curtailment_shutdown_time.R -- row order (ascending threshold) fixed at source -->
```{r shutdown-bands-table}
if (!is.null(params$shutdown_bands)) {
  report_table(rename_display(
    params$shutdown_bands,
    stats::setNames(
      c("Thresh. (rpm)", "Reached", sprintf("%% < %ss", params$shutdown_time_low_cut), sprintf("%% > %ss", params$shutdown_time_high_cut)),
      c("threshold", "n_reached", "pct_below_cut", "pct_above_cut")
    )
  ))
}
```

### Time to Threshold Distribution

<!-- Source: plot_time_to_threshold(), R/curtailment_shutdown_time.R -->
```{r shutdown-plot, fig.width=7, fig.height=6}
if (!is.null(params$shutdown_plot)) print(params$shutdown_plot)
```

## No-Response Events

A no-response event is a curtailment, at or above the cut-in speed, for which no decline of `r params$curtailment_latency_decline_pct * 100`% or more was detected within the allowance window (up to `r params$shutdown_time_buffer_sec` s past the end of the curtailment order), by turbine.

<!-- Source: summarise_latency_by_turbine(latency_dt), R/curtailment_response_latency.R -->
```{r no-response-turbine-table}
if (!is.null(params$latency_by_turbine)) {
  report_table(
    rename_display(
      drop_cols(params$latency_by_turbine, c(
        "n_curtailments", "n_no_data", "pct_no_data", "n_known",
        "n_below_cutin", "pct_below_cutin", "n_reached", "pct_reached",
        "mean_latency_sec", "median_latency_sec"
      )),
      c(
        turbine = "Turbine", n_eligible = "Curtailments",
        n_no_response = "No Response", pct_no_response = "% No Response"
      )
    ),
    max_col_width_cm = 2.5
  )
}
```

## Example Response Profiles

Illustrative examples: RPM profile of individual curtailments, with the curtailment start and stop overlaid, for a window of `r params$curtailment_example_window_before_min` minute(s) before and `r params$curtailment_example_window_after_min` minutes after the curtailment start -- examples below are the most illustrative available (slowest: the longest latencies; no-response: the most recent), not a random or representative sample. Both example categories are always shown below, with the underlying counts, even when there are no examples to plot for a given category this month. Full detail is in the accompanying workbook (`r params$xlsx_curtailment_examples`).

```{r no-response-examples-heading, results='asis'}
cat(sprintf("### No-Response Events (%s example(s))\n\n", params$n_no_response_examples))
```
<!-- Source: select_latency_examples(latency_dt, "no_response"), plot_curtailment_events_rpm(), R/curtailment_forensic_trace.R -->
```{r no-response-examples-plot, fig.width=6.30, fig.height=5.91, results='asis'}
if (!is.null(params$no_response_examples_plot)) {
  print(params$no_response_examples_plot)
} else {
  cat("No no-response events were recorded in this reporting period -- no example plot is shown.\n\n")
}
```

```{r slowest-examples-heading, results='asis'}
cat(sprintf("### Slowest Responses (%s example(s))\n\n", params$n_slowest_examples))
```
<!-- Source: select_latency_examples(latency_dt, "slowest"), plot_curtailment_events_rpm(), R/curtailment_forensic_trace.R -->
```{r slowest-examples-plot, fig.width=6.30, fig.height=5.91, results='asis'}
if (!is.null(params$slowest_response_examples_plot)) {
  print(params$slowest_response_examples_plot)
} else {
  cat("No curtailments with a detected response were available in this reporting period -- no example plot is shown.\n\n")
}
```

# Safe Distance (KNE Methodology)

Distance between the triggering track and the turbine at the moment of curtailment, compared against the KNE reference line (`r params$safe_dist_reference_line_m` m), by priority species. A turbine's estimated time-to-stop-safely uses `r params$safe_dist_rpm_threshold` rpm as the "stopped" threshold; a turbine already below `r params$safe_dist_already_slowing_rpm` rpm at the moment of the signal is treated as already slowing from a previous curtailment, not at full operating speed.

## Overall

<!-- Source: summary_safe_dist$overall <- summarise_safe_distance(safe_dist_dt, prioritysp)$overall, R/curtailment_safe_distance.R (safe_dist_dt from compute_safe_distance()) -->
```{r safe-dist-overall-table}
if (!is.null(params$safe_dist_overall)) {
  report_table(
    rename_display(
      params$safe_dist_overall,
      c(n = "N", n_ok = "OK", n_crit = "Critical", pct_ok = "% OK",
        mean_time_to_threshold_sec = "Mean React. Time (s)", mean_avg_speed_ms = "Mean Track Speed (m/s)",
        pct_already_slowing = "% Already Slowing",
        mean_min_safe_dist_m = "Mean Safe Dist. (m)", median_min_safe_dist_m = "Median Safe Dist. (m)")
    ),
    col_widths_cm = c(
      "Mean React. Time (s)" = 2, "Mean Track Speed (m/s)" = 2, "% Already Slowing" = 2,
      "Mean Safe Dist. (m)" = 2, "Median Safe Dist. (m)" = 2
    )
  )
}
```

## By Species

Mean/Median Safe Dist. (m) is the reaction time to reach the RPM threshold multiplied by that track's own flight speed -- a low value can come from a fast reaction, a slow-flying bird (Mean Track Speed), or the turbine already slowing down from an earlier curtailment order at the moment this one triggered (% Already Slowing), not necessarily from this specific signal being answered unusually fast.

<!-- Source: summary_safe_dist$by_species <- summarise_safe_distance(safe_dist_dt, prioritysp)$by_species, R/curtailment_safe_distance.R -- mean_time_to_threshold_sec/mean_avg_speed_ms/pct_already_slowing added at source to explain low mean_min_safe_dist_m values -->
```{r safe-dist-species-table}
if (!is.null(params$safe_dist_by_species)) {
  report_table(
    rename_display(
      params$safe_dist_by_species,
      c(species = "Species", n = "N", n_ok = "OK", n_crit = "Critical", pct_ok = "% OK",
        mean_time_to_threshold_sec = "Mean React. Time (s)", mean_avg_speed_ms = "Mean Track Speed (m/s)",
        pct_already_slowing = "% Already Slowing",
        mean_min_safe_dist_m = "Mean Safe Dist. (m)", median_min_safe_dist_m = "Median Safe Dist. (m)")
    ),
    col_widths_cm = c(
      "Mean React. Time (s)" = 2, "Mean Track Speed (m/s)" = 2, "% Already Slowing" = 2,
      "Mean Safe Dist. (m)" = 2, "Median Safe Dist. (m)" = 2
    )
  )
}
```

## Distribution

<!-- Source: plot_safe_distance_hist(), R/curtailment_safe_distance.R -->
```{r safe-dist-plot, fig.width=6.30, fig.height=params$safe_dist_plot_height_in}
if (!is.null(params$safe_dist_plot)) print(params$safe_dist_plot)
```

# Bi-Directional ID Transitions

Curtailments triggered by a species reclassification within the same track, in both directions (priority-to-nonpriority and nonpriority-to-priority) -- global, across all non-priority species together, not any single species. A reclassification is considered "late" when it happens more than `r params$id_transition_late_time_sec` s after the curtailment start, or when the track was already within `r params$track_proximity_threshold_m` m of the turbine at the moment of reclassification.

## Risk by Direction

- **P to NP (unnecessary curtailment)**: curtailment triggered while classified as priority, but the track's final classification was non-priority -- turbine stopped unnecessarily (production cost).
- **NP to P, no curtailment (near)**: reclassified to a priority species, no curtailment ever triggered, and the track was already within the proximity threshold at that moment -- the most concerning case.
- **NP to P, no curtailment (far)**: same, but the track was still far from any turbine when reclassified -- descriptive, not necessarily concerning on its own.
- **NP to P, late curtailment**: curtailment was triggered, but later than the agreed time or distance criterion.
- **No risk**: no meaningful transition risk detected (single-species track, or reclassification with a timely curtailment).

<!-- Source: monthly_id_risk_summary$by_direction <- summarise_id_transition_risk(monthly_id_risk_dt, curtl_dt)$by_direction, R/id_transitions.R (monthly_id_risk_dt from classify_id_transition_risk()) -->
```{r id-risk-table}
if (!is.null(params$id_risk_by_direction)) {
  report_table(rename_display(
    recode_values(params$id_risk_by_direction, "risk_direction", c(
      P_to_NP_unnecessary_curtailment = "P to NP (unnecessary curtailment)",
      NP_to_P_no_curtailment_near     = "NP to P, no curtailment (near)",
      NP_to_P_no_curtailment_far      = "NP to P, no curtailment (far)",
      NP_to_P_late_curtailment        = "NP to P, late curtailment",
      no_risk                         = "No risk"
    )),
    c(risk_direction = "Direction", n_tracks = "Tracks", n_multi_id_tracks = "Multi-ID Tracks", pct_of_multi_id = "% of Multi-ID")
  ))
}
```

<!--
9.2 e' opcional (run_sections_monthly$id_confusion, DESLIGADA por omissao
em monthlyReportSettings_BSH.R/_DGY.R) -- analise pontual para a(s) especie(s) em
id_confusion_species_of_interest (Egyptian-Vulture e Steppe-Eagle por
omissao), nao uma metrica de rotina mensal. Quando desligada,
params$id_confusion_general fica NULL e todo o subsection (titulo, texto e
tabela) desaparece do documento -- nao so' a tabela -- por isso o
titulo/texto tambem estao dentro deste chunk condicional (results='asis'),
nao como markdown normal. So' mostra pares > 1% dos tracks multi-ID (ver
filtro no chunk id-confusion-table, abaixo) -- pares muito raros (1-2
tracks em milhares) ficam so' no xlsx.
-->
```{r id-confusion-heading, results='asis'}
if (!is.null(params$id_confusion_general)) {
  cat(sprintf("## 9.2 Species Confusion (%s)\n\n", params$id_confusion_species))
  cat(sprintf(
    "Other species recorded within the same track as %s (all tracks, not only curtailment-triggering ones), for pairs above 1%% of multi-ID tracks in scope.\n\n",
    params$id_confusion_species
  ))
}
```

<!-- Source: monthly_id_confusion_summary$confusion_general <- summarise_species_confusion(), R/id_transitions.R -->
```{r id-confusion-table}
if (!is.null(params$id_confusion_general) && nrow(params$id_confusion_general) > 0) {
  dt <- params$id_confusion_general[params$id_confusion_general$pct_of_multi_id_tracks > 1, ]
  if (nrow(dt) > 0) {
    report_table(rename_display(
      dt,
      c(species = "Species", other_species = "Other Species", n_tracks = "Tracks", pct_of_multi_id_tracks = "% of Multi-ID")
    ))
  }
}
```

# Biological Flight Metrics

Flight speed and flight height per species, for tracks with at least `r params$flight_min_track_points` recorded points and a flight speed between `r params$flight_speed_ms_min` and `r params$flight_speed_ms_max` m/s.

## Flight Speed by Species

<!-- Source: summarise_flight_speed(monthly_flight_base_dt), R/bio_flight_metrics.R (monthly_flight_base_dt from flight_metrics_base()) -->
```{r flight-speed-table}
if (!is.null(params$flight_speed_by_species)) {
  report_table(rename_display(
    drop_cols(params$flight_speed_by_species, c("min_speed_ms", "max_speed_ms")),
    c(spec = "Species", n = "N", mean_speed_ms = "Mean (m/s)", median_speed_ms = "Median (m/s)", sd_speed_ms = "SD (m/s)")
  ))
}
```

## Flight Height by Species

Mean and standard deviation of flight height, plus the % of records within the rotor-swept risk zone (`r params$riskHeight_lower`-`r params$riskHeight_upper` m).

<!-- Source: summarise_flight_height(monthly_flight_base_dt, risk_height_lower, risk_height_upper), R/bio_flight_metrics.R -->
```{r flight-height-table}
if (!is.null(params$flight_height_by_species)) {
  # as.data.frame() primeiro -- params$flight_height_by_species pode ser
  # data.table, onde df[, char_vector] tem semantica ambigua/dependente de
  # versao para seleccao de colunas (ao contrario de data.frame, sem
  # ambiguidade); os outros helpers (rename_display/drop_cols) ja fazem
  # este as.data.frame() internamente, so' este subset manual precisava
  dt <- as.data.frame(params$flight_height_by_species)
  dt <- dt[, intersect(c("spec", "mean_height_m", "sd_height_m", "pct_in_risk_zone"), names(dt)), drop = FALSE]
  report_table(rename_display(
    dt,
    c(spec = "Species", mean_height_m = "Mean (m)", sd_height_m = "SD (m)", pct_in_risk_zone = "% in Risk Zone")
  ))
}
```

## Distribution

<!-- Source: plot_flight_metrics_distribution(), R/bio_flight_metrics.R -->
```{r flight-metrics-plot, fig.width=6.30, fig.height=5.91}
if (!is.null(params$flight_metrics_plot)) print(params$flight_metrics_plot)
```

# Minimum Individuals per Time Bin

Minimum number of distinct individuals per priority species detected in the same `r params$min_individuals_bin_min`-minute time bin (2 tracks count as 1 individual when within `r params$min_individuals_merge_dist_m` m of each other), farm-wide, summarised by day.

## Summary

<!-- Source: summarise_min_individuals(monthly_min_indiv_bins_dt), R/track_min_individuals.R (monthly_min_indiv_bins_dt from count_min_individuals_per_bin()) -->
```{r min-indiv-summary-table}
if (!is.null(params$min_indiv_summary)) {
  report_table(rename_display(
    params$min_indiv_summary,
    c(spec = "Species", n_bins = "Bins", peak_individuals = "Peak Individuals",
      peak_bin_start = "Peak Time", mean_individuals_nonzero = "Mean (Non-zero Bins)")
  ))
}
```

## Daily Peak, by Species

<!-- Source: plot_daily_max_individuals(monthly_min_indiv_daily_dt, species_sel = prioritysp, date_breaks = "1 week"), R/track_min_individuals.R (monthly_min_indiv_daily_dt from summarise_daily_max_individuals()) -->
```{r min-indiv-daily-plot, fig.width=6.30, fig.height=8.66}
if (!is.null(params$min_indiv_daily_plot)) print(params$min_indiv_daily_plot)
```

# Annexes

The full detail behind each table above (including all rows and columns, not only the summaries shown here) is provided as separate files in the same output folder as this report, one workbook/plot set per section: data summary, temporal coverage (including the turbine-level Curtailments/SCADA overlap workbook and plot, section 1.2), system availability (including the turbine-level spatial availability table), observed species, curtailments by species, short-track curtailments, curtailment response assessment (including the curtailment-duration-by-status breakdown, section 6), shutdown time, safe distance, ID transitions and species confusion, biological flight metrics, and minimum individuals per bin.
