---
title: "`r params$title`"
output: word_document
params:
  title: ""
  project_ref: ""
  report_start: ""
  report_end: ""
  analysis_date: ""
  username: ""

  availability_by_idf: !r NULL
  availability_plot_cal: !r NULL
  availability_plot_freq: !r NULL

  coverage_turbine_summary: !r NULL
  coverage_idf_summary: !r NULL

  assess_by_status: !r NULL
  assess_by_turbine: !r NULL

  shutdown_by_turbine: !r NULL
  shutdown_bands: !r NULL
  shutdown_plot: !r NULL

  coverage3d_by_turbine: !r NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Mesmo helper de formatacao de tabelas do report_template.rmd antigo
# (scripts_IDF/), para manter o estilo visual consistente.
report_table <- function(x, caption = NULL) {
  ft <- flextable::flextable(as.data.frame(x)) |>
    flextable::theme_box() |>
    flextable::bg(part = "header", bg = "gray85") |>
    flextable::bold(part = "header") |>
    flextable::fontsize(size = 9, part = "header") |>
    flextable::fontsize(size = 9, part = "body") |>
    flextable::align(align = "center", part = "header") |>
    flextable::valign(valign = "center", part = "all") |>
    flextable::autofit()
  if (!is.null(caption)) ft <- flextable::set_caption(ft, caption)
  ft
}
```

**`r params$project_ref`**

Report period: `r params$report_start` to `r params$report_end`
Analysis date: `r params$analysis_date`
Technician: `r params$username`

---

# 1. System Availability (Heartbeats)

Daylight-time availability of IDF units, based on heartbeat signals.

```{r availability-table}
if (!is.null(params$availability_by_idf)) report_table(params$availability_by_idf)
```

```{r availability-cal, fig.width=9, fig.height=4}
if (!is.null(params$availability_plot_cal)) print(params$availability_plot_cal)
```

```{r availability-freq, fig.width=6, fig.height=3}
if (!is.null(params$availability_plot_freq)) print(params$availability_plot_freq)
```

# 2. Data Coverage

Temporal overlap between Curtailments and SCADA (by turbine), and Heartbeats coverage (by IDF unit). Full download history, not limited to the report period above.

```{r coverage-turbine-table}
if (!is.null(params$coverage_turbine_summary)) report_table(params$coverage_turbine_summary)
```

```{r coverage-idf-table}
if (!is.null(params$coverage_idf_summary)) report_table(params$coverage_idf_summary)
```

# 3. Curtailment Response Assessment

Whether SCADA-recorded RPM dropped as expected in response to curtailment signals (tight 2s baseline tolerance).

```{r assess-status-table}
if (!is.null(params$assess_by_status)) report_table(params$assess_by_status)
```

```{r assess-turbine-table}
if (!is.null(params$assess_by_turbine)) report_table(params$assess_by_turbine)
```

# 4. Shutdown Time

Time from curtailment signal to reaching 2 / 1 / 0 rpm, by turbine.

```{r shutdown-turbine-table}
if (!is.null(params$shutdown_by_turbine)) report_table(params$shutdown_by_turbine)
```

```{r shutdown-bands-table}
if (!is.null(params$shutdown_bands)) report_table(params$shutdown_bands)
```

```{r shutdown-plot, fig.width=7, fig.height=6}
if (!is.null(params$shutdown_plot)) print(params$shutdown_plot)
```

# 5. 3D Coverage (Topography-corrected)

Coverage of the risk airspace around each turbine, corrected for terrain, based on IDF bird track detections.

```{r coverage3d-table}
if (!is.null(params$coverage3d_by_turbine)) report_table(params$coverage3d_by_turbine)
```

Note: interactive 3D plots are saved separately as HTML files (folder `coverage_3d/`) and are not embedded in this document.
