---
title: "`r params$title`"
output: word_document
params:
  title: ""
  project_ref: ""
  report_start: ""
  report_end: ""
  analysis_date: ""
  username: ""
  code_version: ""

  availability_by_idf: !r NULL
  availability_plot_cal: !r NULL
  availability_plot_freq: !r NULL

  coverage_turbine_summary: !r NULL
  coverage_idf_summary: !r NULL

  latency_by_turbine: !r NULL
  latency_bands: !r NULL
  latency_plot: !r NULL
  latency_n_below_cutin: !r NULL
  latency_pct_below_cutin: !r NULL

  shutdown_by_turbine: !r NULL
  shutdown_bands: !r NULL
  shutdown_plot: !r NULL

  coverage3d_by_turbine: !r NULL

  safe_dist_overall: !r NULL
  safe_dist_by_species: !r NULL
  safe_dist_plot: !r NULL

  no_response_examples_plot: !r NULL
  slowest_response_examples_plot: !r NULL
  n_no_response_examples: !r NULL
  n_slowest_examples: !r NULL

  fatality_signal_counts: !r NULL
  fatality_top_candidates: !r NULL
  fatality_window_response_summary: !r NULL
  fatality_abundance_pre_post: !r NULL

  risk_cluster_map: !r NULL
  risk_cluster_summary: !r NULL
  risk_fatality_summary: !r NULL

  species_activity_manual: !r NULL
  species_risk_height_manual: !r NULL
  incident_risk_context_manual: !r NULL

  stat_cluster_map: !r NULL
  stat_cluster_summary: !r NULL
  stat_risk_summary: !r NULL

  species_activity_stat: !r NULL
  species_risk_height_stat: !r NULL
  incident_risk_context_stat: !r NULL

  min_indiv_summary: !r NULL
  min_indiv_plot_daily: !r NULL

  n_turbines_total: !r NULL
  n_idf_total: !r NULL

  # Nomes (basename) dos xlsx de anexo -- 1 por tabela, para a frase "ver
  # anexo ...xlsx" logo apos cada tabela do relatorio.
  xlsx_availability: !r NULL
  xlsx_coverage_turbine: !r NULL
  xlsx_coverage_idf: !r NULL
  xlsx_latency: !r NULL
  xlsx_shutdown: !r NULL
  xlsx_safe_dist: !r NULL
  xlsx_coverage3d: !r NULL
  xlsx_fatality: !r NULL
  xlsx_risk_cluster_patterns: !r NULL
  xlsx_risk_critical_zone: !r NULL
  xlsx_stat_cluster_patterns: !r NULL
  xlsx_stat_critical_zone: !r NULL
  xlsx_species_risk_manual: !r NULL
  xlsx_species_risk_stat: !r NULL
  xlsx_curtailment_examples: !r NULL
  xlsx_min_indiv: !r NULL

  # Literais de configuracao (userSettings_BSH.R) usados so' para texto
  # descritivo -- cada secção que aplica um threshold/cut-off mostra o
  # VALOR concreto usado na analise, nao so' o nome do parametro.
  heartbeat_interval_min: !r NULL
  heartbeat_offline_gap_min: !r NULL

  curtailment_start_end_gap_sec: !r NULL
  curtailment_max_next_gap_sec: !r NULL
  curtailment_drop_pct_threshold: !r NULL
  safe_shutdown_rpm: !r NULL

  shutdown_time_thresholds: !r NULL
  shutdown_time_low_cut: !r NULL
  shutdown_time_high_cut: !r NULL
  shutdown_time_buffer_sec: !r NULL

  curtailment_latency_decline_pct: !r NULL
  curtailment_cutin_rpm: !r NULL

  curtailment_example_window_before_min: !r NULL
  curtailment_example_window_after_min: !r NULL

  safe_dist_reference_line_m: !r NULL
  safe_dist_rpm_threshold: !r NULL
  safe_dist_already_slowing_rpm: !r NULL

  track_proximity_threshold_m: !r NULL
  fatality_post_incident_days: !r NULL

  flight_min_track_points: !r NULL
  flight_speed_ms_min: !r NULL
  flight_speed_ms_max: !r NULL
  risk_height_lower: !r NULL
  risk_height_upper: !r NULL

  cluster_max_dist_m: !r NULL
  cluster_perm_n: !r NULL

  min_individuals_bin_min: !r NULL
  min_individuals_merge_dist_m: !r NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Tabela flextable com o estilo visual do relatorio -- mesmos helpers de
# report/monthly_report_template.rmd, portados para aqui para o relatorio
# anual seguir a mesma convencao visual (arredondamento, largura de coluna,
# renomeacao para apresentacao). round_display() corre sempre primeiro,
# aqui dentro -- nenhuma tabela do relatorio precisa de a chamar manualmente.
report_table <- function(x, caption = NULL, max_col_width_cm = NULL, col_widths_cm = NULL) {
  ft <- flextable::flextable(round_display(x)) |>
    flextable::theme_box() |>
    flextable::bg(part = "header", bg = "gray85") |>
    flextable::bold(part = "header") |>
    flextable::fontsize(size = 9, part = "header") |>
    flextable::fontsize(size = 9, part = "body") |>
    flextable::align(align = "center", part = "header") |>
    flextable::valign(valign = "center", part = "all") |>
    flextable::autofit()
  if (!is.null(max_col_width_cm)) ft <- cap_col_width(ft, max_col_width_cm)
  if (!is.null(col_widths_cm)) ft <- set_col_max_width(ft, col_widths_cm)
  if (!is.null(caption)) ft <- flextable::set_caption(ft, caption)
  ft
}

# Arredonda, so' para apresentacao no docx, cada coluna numerica que tenha
# algum valor nao-inteiro para `digits` casas decimais (2 por omissao) --
# colunas so' com valores inteiros (contagens) ficam como estao. Excecao: se
# arredondar a `digits` casas desse 0 mas o valor real nao e' zero, estende
# casas decimais ate aparecer o 1o digito significativo (ex: 0.001), para
# nao mostrar "0.00" nalgo que na realidade nao e' zero. Devolve os valores
# ja como texto formatado (sprintf) -- os exports xlsx (feitos a partir dos
# objetos originais, nao deste helper) mantêm sempre os valores tal como
# calculados pelas funcoes de analise.
round_display <- function(x, digits = 2) {
  x <- as.data.frame(x)
  for (col in names(x)) {
    v <- x[[col]]
    if (!is.numeric(v) || is.integer(v)) next
    if (all(v == round(v), na.rm = TRUE)) next
    x[[col]] <- vapply(v, function(val) {
      if (is.na(val)) return(NA_character_)
      d <- digits
      while (round(val, d) == 0 && val != 0 && d < 6) d <- d + 1
      sprintf(paste0("%.", d, "f"), val)
    }, character(1))
  }
  x
}

cap_col_width <- function(ft, max_width_cm = 2) {
  # dim() (nao flextable::dim()) -- dim.flextable e' um metodo S3 registado
  # pelo flextable no generico base dim(), nao necessariamente exportado como
  # simbolo chamavel via flextable::dim()
  widths_in <- dim(ft)$widths
  capped_cm <- pmin(widths_in * 2.54, max_width_cm)
  flextable::width(ft, j = seq_along(capped_cm), width = capped_cm, unit = "cm")
}

# Como cap_col_width(), mas por coluna -- widths_cm e' um vector nomeado
# c("Nome da Coluna" = largura_maxima_cm, ...), usando os nomes ja'
# apresentados (apos rename_display()). So' encolhe (nunca alarga) as
# colunas indicadas ate' esse maximo; colunas nao mencionadas ficam como o
# autofit() as deixou. Nomes que nao existirem na tabela sao ignorados.
set_col_max_width <- function(ft, widths_cm) {
  widths_in <- dim(ft)$widths
  idx <- match(names(widths_cm), ft$col_keys)
  hit <- !is.na(idx)
  if (any(hit)) {
    capped_cm <- pmin(widths_in[idx[hit]] * 2.54, unname(widths_cm[hit]))
    ft <- flextable::width(ft, j = idx[hit], width = capped_cm, unit = "cm")
  }
  ft
}

# Renomeia colunas so' para APRESENTACAO no docx -- os exports em xlsx
# (annexos) usam sempre os nomes tecnicos originais dos objetos R. mapping:
# c(nome_original = "Nome Legivel"); colunas nao mencionadas ficam como estao.
rename_display <- function(x, mapping) {
  x <- as.data.frame(x)
  idx <- match(names(mapping), names(x))
  hit <- !is.na(idx)
  names(x)[idx[hit]] <- unname(mapping)[hit]
  x
}

# Remove colunas da tabela apresentada no docx (o xlsx correspondente, feito
# a partir do objeto original nao filtrado, continua completo)
drop_cols <- function(x, cols) {
  x <- as.data.frame(x)
  x[, setdiff(names(x), cols), drop = FALSE]
}

# Substitui VALORES (nao nomes de coluna) de uma coluna categorica por
# rotulos legiveis
recode_values <- function(x, col, mapping) {
  x <- as.data.frame(x)
  hit <- x[[col]] %in% names(mapping)
  x[[col]][hit] <- unname(mapping[x[[col]][hit]])
  x
}

# Frase-padrao, logo apos cada tabela, a apontar para o xlsx de anexo com o
# detalhe completo (todas as linhas/colunas) -- pedido do Paulo (2026-08)
# para toda tabela do relatorio, nao so' as ja' identificadas como resumos
# reduzidos. Chamar APENAS num chunk results='asis' proprio, separado do
# chunk que desenha a tabela (report_table() depende do auto-print do
# knit_print.flextable, que so' funciona corretamente quando essa e' a
# UNICA expressao visivel do bloco -- ver nota "Cada tabela/plot..." acima).
annex_note <- function(xlsx_name) {
  if (!is.null(xlsx_name)) {
    cat(sprintf("\n*The full table is available in the accompanying workbook: `%s`.*\n", xlsx_name))
  }
}
```

<!--
Cada tabela/plot abaixo tem, imediatamente acima do chunk que a produz, um
comentario "Source: ..." a apontar para a funcao R (e ficheiro) que calcula
o objeto correspondente em IDF_analysis.R -- usar isso para encontrar
rapidamente onde ajustar cada tabela/plot sem ter de procurar pelo nome do
param em todo o script. Estes comentarios HTML nao aparecem no .docx gerado.

Cada tabela/plot tem tambem a sua propria subsecção (##), com 1 frase a
identificar o objeto, mesmo quando 2 tabelas pertencem à mesma secção -- 2
flextables em chunks consecutivos sem nenhum paragrafo de texto a
separa-los tendem a sair "coladas" no docx (dificeis de selecionar/mover/
editar independentemente no Word). Uma frase de texto entre elas garante
uma quebra de paragrafo real a separa-las (mesma correcao aplicada ao
relatorio mensal, report/monthly_report_template.rmd).

Plots com eixo de datas usam fig.width=6.30 (=16cm) por omissao, com
expand=c(0,0) e breaks mais curtos definidos a montante em R (ver
comentarios "Source:"), para nao ter datas fora do periodo coberto e para
os rotulos do eixo ficarem legiveis mesmo num historico de varios meses.
-->

**`r params$project_ref`**

Report period: `r params$report_start` to `r params$report_end`

Analysis date: `r params$analysis_date`

Responsible Team: `r params$username`

Code version: `r params$code_version`

This report is descriptive and fully automated, generated end-to-end by an R code pipeline. It presents the metrics produced by the IDF analysis pipeline over the full project history to date, without further interpretation, except where an explicit threshold (e.g. the KNE safe-distance reference line, shutdown-time bands) is already part of the pre-defined methodology.

---

# System Availability (Heartbeats)

Heartbeats are expected every `r params$heartbeat_interval_min` minutes; an IDF unit is considered offline once the gap since its last heartbeat exceeds `r params$heartbeat_offline_gap_min` minutes (at least 2 consecutive heartbeats missed). Full project history to date.

## Availability by IDF Unit

<!-- Source: idf_availability_summary$by_idf <- summarise_availability(idf_availability_dt), R/availability_daylight.R -->
```{r availability-table}
if (!is.null(params$availability_by_idf)) {
  report_table(
    rename_display(
      drop_cols(params$availability_by_idf, c("daylight_mins_total", "days_covered", "offline_mins_total", "availability_pct")),
      c(idf = "IDF Unit", monitoring_period_pct = "Offline (%)", availability_cat = "Category")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r availability-annex, results='asis'}
annex_note(params$xlsx_availability)
```

## Availability Calendar

Daily offline percentage per IDF unit, laid out as a calendar.

<!-- Source: plot_availability_calendar(), R/availability_daylight.R -->
```{r availability-cal, fig.width=6.30, fig.height=9}
if (!is.null(params$availability_plot_cal)) print(params$availability_plot_cal + ggplot2::theme(legend.position = "bottom"))
```

## Availability Frequency

Count of IDF units per daylight-availability category.

<!-- Source: plot_availability_frequency(), R/availability_daylight.R -->
```{r availability-freq, fig.width=6.30, fig.height=3.5}
if (!is.null(params$availability_plot_freq)) print(params$availability_plot_freq)
```

# Data Coverage

Temporal overlap between Curtailments and SCADA (by turbine), and Heartbeats coverage (by IDF unit), over the full download history to date (not limited to the report period above).

## Curtailments / SCADA Overlap by Turbine

Number of days with data on each side, and the days where both overlap, per turbine.

<!-- Source: coverage_turbine_summary <- overlap_summary_by_turbine(coverage_turbine_dt, "Curtailments", "SCADA"), R/data_coverage.R -- pct_overlap_of_total (days_overlap/total_days) is computed here in the Rmd, not in R, purely for display -->
```{r coverage-turbine-prep, include=FALSE}
cov_turbine_dt <- NULL
if (!is.null(params$coverage_turbine_summary)) {
  cov_turbine_dt <- as.data.frame(params$coverage_turbine_summary)
  cov_turbine_dt$pct_overlap_of_total <- round(100 * cov_turbine_dt$days_overlap / cov_turbine_dt$total_days, 1)
}
```
```{r coverage-turbine-text, results='asis'}
if (!is.null(cov_turbine_dt) && nrow(cov_turbine_dt) > 0) {
  pct_of_farm <- ""
  if (!is.null(params$n_turbines_total) && params$n_turbines_total > 0) {
    pct_of_farm <- sprintf(" (%.0f%% of the %d turbines in the farm)", 100 * nrow(cov_turbine_dt) / params$n_turbines_total, params$n_turbines_total)
  }
  cat(sprintf(
    "%d turbine(s)%s have overlapping Curtailments/SCADA data, with %% Overlap ranging from %.1f%% to %.1f%%.\n\n",
    nrow(cov_turbine_dt), pct_of_farm,
    min(cov_turbine_dt$pct_overlap_of_total, na.rm = TRUE), max(cov_turbine_dt$pct_overlap_of_total, na.rm = TRUE)
  ))
}
```
```{r coverage-turbine-table}
if (!is.null(cov_turbine_dt)) {
  report_table(
    rename_display(
      drop_cols(cov_turbine_dt, c("pct_a_with_overlap", "pct_b_with_overlap")),
      c(turbine = "Turbine", total_days = "Total Days", days_a = "Days Curtailments",
        days_b = "Days SCADA", days_overlap = "Days Overlap", pct_overlap_of_total = "% Overlap")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r coverage-turbine-annex, results='asis'}
annex_note(params$xlsx_coverage_turbine)
```

## Heartbeats Coverage by IDF Unit

Days with heartbeat data, and days missing, per IDF unit.

<!-- Source: coverage_idf_summary <- presence_summary_by_idf(coverage_idf_dt), R/data_coverage.R -->
```{r coverage-idf-text, results='asis'}
if (!is.null(params$coverage_idf_summary) && nrow(params$coverage_idf_summary) > 0) {
  dt <- params$coverage_idf_summary
  pct_of_total <- ""
  if (!is.null(params$n_idf_total) && params$n_idf_total > 0) {
    pct_of_total <- sprintf(" (%.0f%% of the %d IDF units in the farm)", 100 * nrow(dt) / params$n_idf_total, params$n_idf_total)
  }
  cat(sprintf(
    "%d IDF unit(s)%s have heartbeat data, with %% Missing ranging from %.1f%% to %.1f%%.\n\n",
    nrow(dt), pct_of_total, min(dt$pct_missing, na.rm = TRUE), max(dt$pct_missing, na.rm = TRUE)
  ))
}
```
```{r coverage-idf-table}
if (!is.null(params$coverage_idf_summary)) {
  report_table(
    rename_display(
      params$coverage_idf_summary,
      c(idf = "IDF Unit", start = "From", end = "To", days_with_data = "Days with Data",
        total_days = "Total Days", days_missing = "Days Missing", pct_missing = "% Missing")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r coverage-idf-annex, results='asis'}
annex_note(params$xlsx_coverage_idf)
```

# Curtailment Response & Latency

Whether SCADA-recorded RPM dropped as expected in response to curtailment signals, over the full project history to date. The SCADA baseline immediately before/after each signal is trusted only within `r params$curtailment_start_end_gap_sec` s. A response is considered to have started once RPM has dropped by at least `r params$curtailment_latency_decline_pct * 100`% from its value at the start of the curtailment order; a turbine is considered stopped once RPM falls below `r params$safe_shutdown_rpm`. Both response latency and shutdown time below allow up to `r params$shutdown_time_buffer_sec` s past the end of the curtailment order for this to happen. Curtailments with an RPM below `r params$curtailment_cutin_rpm` (the cut-in speed, below which the turbine is not producing energy) at the start of the order are excluded from the Response Latency and No-Response Events tables below, since there is no meaningful response to measure on a turbine that was already not operating: `r params$latency_n_below_cutin` curtailments (`r params$latency_pct_below_cutin`% of the curtailments with a valid SCADA baseline) fall in this category over the period covered.

## Response Latency

Time from the curtailment signal to the first SCADA reading showing the decline defined above, by turbine, among curtailments at or above the cut-in speed.

<!-- Source: summarise_latency_by_turbine(latency_dt), R/curtailment_response_latency.R -->
```{r latency-turbine-table}
if (!is.null(params$latency_by_turbine)) {
  report_table(
    rename_display(
      drop_cols(params$latency_by_turbine, c(
        "n_curtailments", "n_below_cutin", "pct_below_cutin", "n_no_response", "pct_no_response"
      )),
      c(
        turbine = "Turbine", n_eligible = "Curtailments", n_reached = "Reached",
        pct_reached = "% Reached", mean_latency_sec = "Mean (s)", median_latency_sec = "Median (s)"
      )
    ),
    max_col_width_cm = 2
  )
}
```
```{r latency-turbine-annex, results='asis'}
annex_note(params$xlsx_latency)
```

### Response Latency Bands

Of the curtailments where a decline was detected, share with latency within each cut-off.

<!-- Source: summarise_latency_bands(latency_dt), R/curtailment_response_latency.R -->
```{r latency-bands-table}
if (!is.null(params$latency_bands)) {
  report_table(rename_display(
    params$latency_bands,
    c(cutoff_sec = "Cut-off (s)", pct_within_cutoff = "% Within Cut-off")
  ))
}
```
```{r latency-bands-annex, results='asis'}
annex_note(params$xlsx_latency)
```

### Response Latency Distribution

<!-- Source: plot_latency_histogram(latency_dt), R/curtailment_response_latency.R -->
```{r latency-plot, fig.width=6.30, fig.height=4}
if (!is.null(params$latency_plot)) print(params$latency_plot)
```

## Shutdown Time

Time from curtailment signal to reaching each RPM threshold, by turbine -- 3 thresholds evaluated: `r paste(params$shutdown_time_thresholds, collapse = ", ")` rpm. Bands below/above the agreed cut-offs are reported as-is, without further interpretation.

### Time to Threshold by Turbine

<!-- Source: summarise_time_to_threshold(tt_dt), R/curtailment_shutdown_time.R -->
```{r shutdown-turbine-table}
if (!is.null(params$shutdown_by_turbine)) {
  report_table(
    rename_display(
      drop_cols(params$shutdown_by_turbine, c("median_time_sec")),
      c(
        turbine = "Turbine", threshold = "Thresh. (rpm)", n_curtailments = "Curtailments",
        n_reached = "Reached", pct_reached = "% Reached", mean_time_sec = "Mean (s)",
        sd_time_sec = "SD (s)", min_time_sec = "Min (s)", max_time_sec = "Max (s)"
      )
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r shutdown-turbine-annex, results='asis'}
annex_note(params$xlsx_shutdown)
```

### Time to Threshold Bands

A curtailment counts as "below cut" when it reached the threshold in under `r params$shutdown_time_low_cut` s (fast), and "above cut" when it took more than `r params$shutdown_time_high_cut` s (slow); cases in between count towards neither band.

<!-- Source: summarise_time_to_threshold_bands(tt_dt), R/curtailment_shutdown_time.R -->
```{r shutdown-bands-table}
if (!is.null(params$shutdown_bands)) {
  report_table(rename_display(
    params$shutdown_bands,
    stats::setNames(
      c("Thresh. (rpm)", "Reached", sprintf("%% < %ss", params$shutdown_time_low_cut), sprintf("%% > %ss", params$shutdown_time_high_cut)),
      c("threshold", "n_reached", "pct_below_cut", "pct_above_cut")
    )
  ))
}
```
```{r shutdown-bands-annex, results='asis'}
annex_note(params$xlsx_shutdown)
```

### Time to Threshold Distribution

<!-- Source: plot_time_to_threshold(), R/curtailment_shutdown_time.R -->
```{r shutdown-plot, fig.width=6.30, fig.height=6}
if (!is.null(params$shutdown_plot)) print(params$shutdown_plot)
```

## No-Response Events

A no-response event is a curtailment, at or above the cut-in speed, for which no decline of `r params$curtailment_latency_decline_pct * 100`% or more was detected within the allowance window (up to `r params$shutdown_time_buffer_sec` s past the end of the curtailment order), by turbine.

<!-- Source: summarise_latency_by_turbine(latency_dt), R/curtailment_response_latency.R -->
```{r no-response-turbine-table}
if (!is.null(params$latency_by_turbine)) {
  report_table(
    rename_display(
      drop_cols(params$latency_by_turbine, c(
        "n_curtailments", "n_below_cutin", "pct_below_cutin", "n_reached", "pct_reached",
        "mean_latency_sec", "median_latency_sec"
      )),
      c(
        turbine = "Turbine", n_eligible = "Curtailments",
        n_no_response = "No Response", pct_no_response = "% No Response"
      )
    ),
    max_col_width_cm = 2.5
  )
}
```
```{r no-response-turbine-annex, results='asis'}
annex_note(params$xlsx_latency)
```

```{r example-response-heading, results='asis'}
if (!is.null(params$no_response_examples_plot) || !is.null(params$slowest_response_examples_plot)) {
  cat("## Example Response Profiles\n\n")
  cat(sprintf(
    "Illustrative examples: RPM profile of individual curtailments, with the curtailment start and stop overlaid, for a window of %s minute(s) before and %s minutes after the curtailment start -- examples below are the most illustrative available (slowest: the longest latencies; no-response: the most recent), not a random or representative sample.\n\n",
    params$curtailment_example_window_before_min, params$curtailment_example_window_after_min
  ))
}
```

```{r no-response-examples-heading, results='asis'}
if (!is.null(params$no_response_examples_plot)) cat(sprintf("### No-Response Events (%s example(s))\n\n", params$n_no_response_examples))
```
<!-- Source: select_latency_examples(latency_dt, "no_response"), plot_curtailment_events_rpm(), R/curtailment_forensic_trace.R -->
```{r no-response-examples-plot, fig.width=6.30, fig.height=9}
if (!is.null(params$no_response_examples_plot)) print(params$no_response_examples_plot)
```

```{r slowest-examples-heading, results='asis'}
if (!is.null(params$slowest_response_examples_plot)) cat(sprintf("### Slowest Responses (%s example(s))\n\n", params$n_slowest_examples))
```
<!-- Source: select_latency_examples(latency_dt, "slowest"), plot_curtailment_events_rpm(), R/curtailment_forensic_trace.R -->
```{r slowest-examples-plot, fig.width=6.30, fig.height=9}
if (!is.null(params$slowest_response_examples_plot)) print(params$slowest_response_examples_plot)
```
```{r curtailment-examples-annex, results='asis'}
if (!is.null(params$no_response_examples_plot) || !is.null(params$slowest_response_examples_plot)) annex_note(params$xlsx_curtailment_examples)
```

# Safe Distance (KNE Methodology)

Distance between the triggering track and the turbine at the moment of curtailment, compared against the KNE reference line (`r params$safe_dist_reference_line_m` m), by priority species. A turbine's estimated time-to-stop-safely uses `r params$safe_dist_rpm_threshold` rpm as the "stopped" threshold; a turbine already below `r params$safe_dist_already_slowing_rpm` rpm at the moment of the signal is treated as already slowing from a previous curtailment, not at full operating speed.

## Overall

<!-- Source: summary_safe_dist$overall <- summarise_safe_distance(safe_dist_dt, prioritysp)$overall, R/curtailment_safe_distance.R -->
```{r safe-dist-overall-table}
if (!is.null(params$safe_dist_overall)) {
  report_table(
    rename_display(
      params$safe_dist_overall,
      c(n = "N", n_ok = "OK", n_crit = "Critical", pct_ok = "% OK",
        mean_time_to_threshold_sec = "Mean React. Time (s)", mean_avg_speed_ms = "Mean Track Speed (m/s)",
        pct_already_slowing = "% Already Slowing",
        mean_min_safe_dist_m = "Mean Safe Dist. (m)", median_min_safe_dist_m = "Median Safe Dist. (m)")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r safe-dist-overall-annex, results='asis'}
annex_note(params$xlsx_safe_dist)
```

## By Species

Mean/Median Safe Dist. (m) is the reaction time to reach the RPM threshold multiplied by that track's own flight speed -- a low value can come from a fast reaction, a slow-flying bird (Mean Track Speed), or the turbine already slowing down from an earlier curtailment order at the moment this one triggered (% Already Slowing), not necessarily from this specific signal being answered unusually fast.

<!-- Source: summary_safe_dist$by_species <- summarise_safe_distance(safe_dist_dt, prioritysp)$by_species, R/curtailment_safe_distance.R -->
```{r safe-dist-species-table}
if (!is.null(params$safe_dist_by_species)) {
  report_table(
    rename_display(
      params$safe_dist_by_species,
      c(species = "Species", n = "N", n_ok = "OK", n_crit = "Critical", pct_ok = "% OK",
        mean_time_to_threshold_sec = "Mean React. Time (s)", mean_avg_speed_ms = "Mean Track Speed (m/s)",
        pct_already_slowing = "% Already Slowing",
        mean_min_safe_dist_m = "Mean Safe Dist. (m)", median_min_safe_dist_m = "Median Safe Dist. (m)")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r safe-dist-species-annex, results='asis'}
annex_note(params$xlsx_safe_dist)
```

## Distribution

<!-- Source: plot_safe_distance_hist(), R/curtailment_safe_distance.R -->
```{r safe-dist-plot, fig.width=6.30, fig.height=6}
if (!is.null(params$safe_dist_plot)) print(params$safe_dist_plot)
```

# 3D Coverage (Topography-corrected)

Coverage of the risk airspace around each turbine, corrected for terrain, based on IDF bird track detections.

<!-- Source: summary_cov <- summarise_mesh_coverage(...), R/coverage_3d_topography.R -->
```{r coverage3d-table}
if (!is.null(params$coverage3d_by_turbine)) {
  report_table(rename_display(
    drop_cols(params$coverage3d_by_turbine, c("n_records", "n_valid", "low_sample")),
    c(wtg_id = "Turbine", n_air_mesh = "Air Mesh Cells", n_covered = "Covered Cells", pct_covered = "% Covered")
  ))
}
```
```{r coverage3d-annex, results='asis'}
annex_note(params$xlsx_coverage3d)
```

Note: interactive 3D plots are saved separately as HTML files (folder `coverage_3d/`) and are not embedded in this document.

# Fatality Investigation

Investigation of the known fatality incidents (`r params$track_proximity_threshold_m` m proximity threshold to identify candidate tracks; the recorded incident date is when the carcass was found during a turbine ground survey, not the date of collision, so each incident is investigated over a window of days before that date, not the single day).

## Candidate Tracks by Signal

Count of tracks recorded near each incident's turbine, by signal type (e.g. curtailment triggered vs. not, near vs. far), for the days before each incident.

<!-- Source: fatality_summary$counts_by_signal <- summarise_fatality_tracks(fatality_tracks_dt)$counts_by_signal, R/fatality_track_investigation.R -->
```{r fatality-signal-counts-table}
if (!is.null(params$fatality_signal_counts)) {
  report_table(
    rename_display(
      params$fatality_signal_counts,
      c(incident_id = "Incident", turbine = "Turbine", species = "Species", signal = "Signal",
        n_tracks = "Tracks", pct_of_incident = "% of Incident")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r fatality-signal-counts-annex, results='asis'}
annex_note(params$xlsx_fatality)
```

## Top Candidate Tracks

The tracks most likely associated with each incident -- those whose last recorded position ends closest to the turbine, among the candidate signal types. This is an adjusted summary (Incident, Turbine, Species, Triggered Curtailment and Signal only); the full table (all candidate tracks, including track ID, point counts, distances and timestamps) is in the accompanying workbook.

<!-- Source: fatality_summary$top_candidates <- summarise_fatality_tracks(fatality_tracks_dt)$top_candidates, R/fatality_track_investigation.R -->
```{r fatality-top-candidates-table}
if (!is.null(params$fatality_top_candidates)) {
  dt <- as.data.frame(params$fatality_top_candidates)
  dt <- dt[, intersect(c("incident_id", "turbine", "species", "triggered_curtailment", "signal"), names(dt)), drop = FALSE]
  report_table(rename_display(
    dt,
    c(incident_id = "Incident", turbine = "Turbine", species = "Species",
      triggered_curtailment = "Triggered Curtailment", signal = "Signal")
  ))
}
```
```{r fatality-top-candidates-annex, results='asis'}
annex_note(params$xlsx_fatality)
```

## Curtailment Response Around Each Incident

Response outcome (ok/delayed/missed/no_data, see R/curtailment_response_classify.R) restricted to each incident's turbine and window of days before/after the incident.

<!-- Source: fatality_window_response_summary_dt <- rbindlist over fatality_windows[[id]]$curtailment_response$by_flag, R/fatality_window_analysis.R -->
```{r fatality-window-response-table}
if (!is.null(params$fatality_window_response_summary)) {
  report_table(rename_display(
    params$fatality_window_response_summary,
    c(incident_id = "Incident", response_flag = "Response", n = "N", pct_of_total = "% of Total", pct_of_known = "% of Known")
  ))
}
```
```{r fatality-window-response-annex, results='asis'}
annex_note(params$xlsx_fatality)
```

## Abundance Before/After Each Incident

Minimum-individuals abundance of the incident's species, comparing the `r params$fatality_post_incident_days`-day window after the incident date against the days-before window used for the track investigation above -- descriptive only, a difference may reflect the incident or simply the natural phenology of the migration passing through, no causality is assumed.

<!-- Source: fatality_abundance_pre_post_dt <- rbindlist over fatality_windows[[id]]$abundance <- summarise_individuals_pre_post(), R/fatality_window_analysis.R -->
```{r fatality-abundance-table}
if (!is.null(params$fatality_abundance_pre_post)) {
  report_table(
    rename_display(
      params$fatality_abundance_pre_post,
      c(incident_id = "Incident", period = "Period", n_days = "Days", n_bins = "Bins",
        peak_individuals = "Peak Individuals", mean_individuals = "Mean Individuals")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r fatality-abundance-annex, results='asis'}
annex_note(params$xlsx_fatality)
```

```{r cluster-section-guards, include=FALSE}
# Secção 8 combina a via manual (antigas 7.5-7.8) e a via estatistica
# (antiga secção 8 standalone) num so' capitulo, cada uma na sua propria
# subsecção (8.1/8.2) -- cada uma so' aparece (titulo incluido) quando tem
# conteudo: manual liga/desliga com run_sections$risk_clusters, estatistica
# com run_sections$turbine_clustering (ambas em userSettings_BSH.R).
show_manual_cluster <- !is.null(params$risk_cluster_map) || !is.null(params$risk_cluster_summary) || !is.null(params$risk_fatality_summary) || !is.null(params$species_activity_manual)
show_stat_cluster    <- !is.null(params$stat_cluster_map) || !is.null(params$stat_cluster_summary) || !is.null(params$stat_risk_summary) || !is.null(params$species_activity_stat)
```

```{r cluster-section-heading, results='asis'}
if (show_manual_cluster || show_stat_cluster) {
  cat("# Turbine Clustering & Risk by Sector\n\n")
  cat("Turbines grouped into clusters, 2 independent methods: manual sectors (pre-defined, `manual_turbine_clusters`) and statistical clusters (grouped by distance, max ", params$cluster_max_dist_m, " m between turbines in the same cluster). Each method groups the same underlying curtailment and track data differently; for each, curtailments per cluster, a permutation-test-based risk summary at the incident turbines, and species activity/risk-height exposure by cluster for the fatality-incident species (rank + permutation test, ", params$cluster_perm_n, " permutations where applicable).\n\n", sep = "")
}
```

```{r manual-cluster-heading, results='asis'}
if (show_manual_cluster) cat("## Manual Clustering\n\n")
```

```{r manual-cluster-map-heading, results='asis'}
if (!is.null(params$risk_cluster_map)) cat("### Manual Risk Clusters Map\n\nTurbine sectors as defined manually (`manual_turbine_clusters`), with the incident turbines highlighted.\n\n")
```
<!-- Source: p_map_manual <- plot_turbine_clusters_map(wtg, cluster_dt_manual, ...), R/turbine_spatial_clusters.R -->
```{r risk-cluster-map, fig.width=6.30, fig.height=5.04}
if (!is.null(params$risk_cluster_map)) print(params$risk_cluster_map)
```

```{r manual-cluster-summary-heading, results='asis'}
if (!is.null(params$risk_cluster_summary)) cat("### Curtailments by Manual Sector\n\nTotal curtailments per manual sector, over the full project history.\n\n")
```
<!-- Source: cluster_summary_manual$by_cluster <- summarise_cluster_curtailments(curtl_cl_manual_dt)$by_cluster, R/curtailment_cluster_patterns.R -->
```{r risk-cluster-summary-table}
if (!is.null(params$risk_cluster_summary)) {
  report_table(rename_display(
    params$risk_cluster_summary,
    c(cluster_id = "Sector", n_turbines = "Turbines", n_total = "Curtailments",
      mean_per_turbine = "Mean per Turbine", cluster_rank = "Rank")
  ))
}
```
```{r risk-cluster-summary-annex, results='asis'}
annex_note(params$xlsx_risk_cluster_patterns)
```

```{r manual-risk-summary-heading, results='asis'}
if (!is.null(params$risk_fatality_summary)) cat("### Risk Summary at Incident Turbines\n\nFor each incident's turbine: its share of its manual sector's curtailments (Sector Curtlms.), and its rank among the sector's turbines by that share (Curtlm. Rank).\n\n")
```
<!-- Source: fatality_risk_summary_dt <- merge(critical_zone_manual_dt, perm_manual_dt), IDF_analysis.R section 10.3 (critical_zone_manual_dt from summarise_turbine_critical_zone(), R/turbine_critical_zone_summary.R; perm_manual_dt from permutation_test_marginal_contribution_all(), R/curtailment_cluster_patterns.R) -->
```{r risk-fatality-summary-table}
if (!is.null(params$risk_fatality_summary)) {
  dt <- as.data.frame(params$risk_fatality_summary)
  dt <- dt[, intersect(c("turbine", "n_total", "cluster_rank"), names(dt)), drop = FALSE]
  report_table(rename_display(
    dt,
    c(turbine = "Turbine", n_total = "Sector Curtlms.", cluster_rank = "Curtlm. Rank")
  ))
}
```
```{r risk-fatality-summary-annex, results='asis'}
annex_note(params$xlsx_risk_critical_zone)
```

```{r manual-species-risk-heading, results='asis'}
if (!is.null(params$species_activity_manual) && !is.null(params$species_risk_height_manual)) {
  cat("### Species Activity & Risk-Height Exposure by Cluster\n\n")
  cat(sprintf(
    "Complementary view, independent of curtailments: for the species involved in the known fatality incidents, farm-wide track activity and flight-height risk exposure, by manual sector, over the full project history. Track activity is the number of distinct tracks of that species whose closest-approach turbine falls in that sector; risk-height exposure is the %% of that species' reliable flight-height readings (tracks with at least %s points and a flight speed between %s and %s m/s, in that sector) that fall within the %s-%s m rotor-swept band. Both are ranked per species (rank 1 = highest); a sector ranking high on both is where this species is both most frequently present and most often flying at rotor height, relative to the other sectors -- not a measure of curtailment response or turbine performance.\n\n",
    params$flight_min_track_points, params$flight_speed_ms_min, params$flight_speed_ms_max,
    params$risk_height_lower, params$risk_height_upper
  ))
}
```
<!-- Source: species_activity_manual_dt <- summarise_species_cluster_activity(), species_risk_height_manual_dt <- summarise_species_cluster_risk_height(), R/species_cluster_risk_ranking.R -->
```{r species-risk-manual-table}
if (!is.null(params$species_activity_manual) && !is.null(params$species_risk_height_manual)) {
  dt <- merge(
    as.data.frame(params$species_activity_manual),
    as.data.frame(params$species_risk_height_manual),
    by = c("spec", "cluster_id"), all = TRUE
  )
  dt <- dt[, intersect(c(
    "spec", "cluster_id", "n_tracks", "pct_of_total", "activity_rank",
    "pct_in_risk_zone", "risk_rank"
  ), names(dt)), drop = FALSE]
  dt <- dt[order(dt$spec, dt$activity_rank), ]
  report_table(
    rename_display(
      dt,
      c(spec = "Species", cluster_id = "Sector", n_tracks = "Tracks", pct_of_total = "% of Species Tracks",
        activity_rank = "Activity Rank", pct_in_risk_zone = "% in Risk-Height Zone", risk_rank = "Risk-Height Rank")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r species-risk-manual-annex, results='asis'}
annex_note(params$xlsx_species_risk_manual)
```

```{r manual-incident-risk-context-heading, results='asis'}
if (!is.null(params$incident_risk_context_manual)) cat("#### Risk Context at Incident Turbines\n\nFor each incident's turbine, where its sector falls in the two rankings above -- \"below median\" means that sector ranks in the lower half of sectors for that species on that metric (comparatively less active / less exposed than most other sectors, for that species). This describes relative standing only, using the full project history; it does not establish causality with the incident, and being below median on both metrics does not amount to a validated \"low risk\" threshold -- it only means the baseline activity/exposure data do not contradict treating that sector's risk as comparatively lower than the farm's other sectors.\n\n")
```
<!-- Source: incident_risk_context_manual_dt <- summarise_incident_cluster_risk_context(), R/species_cluster_risk_ranking.R -->
```{r incident-risk-context-manual-table}
if (!is.null(params$incident_risk_context_manual)) {
  report_table(
    rename_display(
      drop_cols(params$incident_risk_context_manual, c("below_median_activity", "below_median_risk_height", "low_baseline_risk_supported")),
      c(incident_id = "Incident", turbine = "Turbine", species = "Species", cluster_id = "Sector",
        n_clusters = "N Sectors", track_activity_rank = "Activity Rank", track_pct_of_total = "% of Species Tracks",
        risk_height_rank = "Risk-Height Rank", pct_in_risk_zone = "% in Risk-Height Zone")
    ),
    max_col_width_cm = 1.5
  )
}
```

```{r manual-incident-risk-context-lead, results='asis'}
if (!is.null(params$incident_risk_context_manual)) cat("Per-incident detail:\n\n")
```

```{r incident-risk-context-manual-text, results='asis'}
if (!is.null(params$incident_risk_context_manual) && nrow(params$incident_risk_context_manual) > 0) {
  dt <- params$incident_risk_context_manual
  cat("\n")
  for (i in seq_len(nrow(dt))) {
    r <- dt[i, ]
    verdict <- if (isTRUE(r$low_baseline_risk_supported)) {
      "its sector is below median on both metrics, so the baseline activity/exposure data do not contradict treating this sector's risk as comparatively lower than the farm's other sectors"
    } else {
      "its sector is not below median on both metrics, so these data do not support treating this sector's risk as comparatively low"
    }
    cat(sprintf(
      "- **%s** (%s, %s): sector %s ranks %s of %s by track activity (%s%% of the species' farm-wide tracks) and %s of %s by time in the risk-height zone (%s%%) -- %s.\n",
      r$incident_id, r$turbine, r$species, r$cluster_id,
      r$track_activity_rank, r$n_clusters, r$track_pct_of_total,
      r$risk_height_rank, r$n_clusters, r$pct_in_risk_zone,
      verdict
    ))
  }
  cat("\n")
}
```

```{r stat-cluster-heading, results='asis'}
if (show_stat_cluster) cat("## Statistical Clustering\n\n")
```

```{r stat-cluster-map-heading, results='asis'}
if (!is.null(params$stat_cluster_map)) cat("### Statistical Clusters Map\n\n")
```
<!-- Source: p_map_stat <- plot_turbine_clusters_map(wtg, cluster_dt_stat, ...), R/turbine_spatial_clusters.R -->
```{r stat-cluster-map, fig.width=6.30, fig.height=5.04}
if (!is.null(params$stat_cluster_map)) print(params$stat_cluster_map)
```

```{r stat-cluster-summary-heading, results='asis'}
if (!is.null(params$stat_cluster_summary)) cat("### Curtailments by Statistical Cluster\n\n")
```
<!-- Source: cluster_summary_stat$by_cluster <- summarise_cluster_curtailments(curtl_cl_stat_dt)$by_cluster, R/curtailment_cluster_patterns.R -->
```{r stat-cluster-summary-table}
if (!is.null(params$stat_cluster_summary)) {
  report_table(rename_display(
    params$stat_cluster_summary,
    c(cluster_id = "Cluster", n_turbines = "Turbines", n_total = "Curtailments",
      mean_per_turbine = "Mean per Turbine", cluster_rank = "Rank")
  ))
}
```
```{r stat-cluster-summary-annex, results='asis'}
annex_note(params$xlsx_stat_cluster_patterns)
```

```{r stat-risk-summary-heading, results='asis'}
if (!is.null(params$stat_risk_summary)) {
  cat("### Risk Summary at Incident Turbines\n\n")
  cat("Same combined view as the manual sectors section above, computed instead over the statistical clusters.\n\n")
}
```
<!-- Source: stat_risk_summary_dt <- merge(critical_zone_stat_dt, perm_stat_dt), IDF_analysis.R section 10.3 -->
```{r stat-risk-summary-table}
if (!is.null(params$stat_risk_summary)) {
  dt <- as.data.frame(params$stat_risk_summary)
  dt <- dt[, intersect(c(
    "turbine", "cluster_id", "n_total", "pct_of_cluster", "cluster_rank",
    "track_pct_of_total", "track_cluster_rank", "observed_pct"
  ), names(dt)), drop = FALSE]
  report_table(
    rename_display(
      dt,
      c(turbine = "Turbine", cluster_id = "Cluster", n_total = "Cluster Curtailments",
        pct_of_cluster = "% of Cluster", cluster_rank = "Curtailment Rank",
        track_pct_of_total = "% of Cluster Tracks", track_cluster_rank = "Track Rank",
        observed_pct = "Observed %")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r stat-risk-summary-annex, results='asis'}
annex_note(params$xlsx_stat_critical_zone)
```

```{r stat-species-risk-heading, results='asis'}
if (!is.null(params$species_activity_stat) && !is.null(params$species_risk_height_stat)) {
  cat("### Species Activity & Risk-Height Exposure by Cluster\n\n")
  cat(sprintf(
    "Same complementary view as the manual sectors section above, computed instead over the statistical clusters: farm-wide track activity and flight-height risk exposure, for the species involved in the known fatality incidents, over the full project history (tracks with at least %s points and a flight speed between %s and %s m/s; risk-height band %s-%s m).\n\n",
    params$flight_min_track_points, params$flight_speed_ms_min, params$flight_speed_ms_max,
    params$risk_height_lower, params$risk_height_upper
  ))
}
```
```{r species-risk-stat-table}
if (!is.null(params$species_activity_stat) && !is.null(params$species_risk_height_stat)) {
  dt <- merge(
    as.data.frame(params$species_activity_stat),
    as.data.frame(params$species_risk_height_stat),
    by = c("spec", "cluster_id"), all = TRUE
  )
  dt <- dt[, intersect(c(
    "spec", "cluster_id", "n_tracks", "pct_of_total", "activity_rank",
    "pct_in_risk_zone", "risk_rank"
  ), names(dt)), drop = FALSE]
  dt <- dt[order(dt$spec, dt$activity_rank), ]
  report_table(
    rename_display(
      dt,
      c(spec = "Species", cluster_id = "Cluster", n_tracks = "Tracks", pct_of_total = "% of Species Tracks",
        activity_rank = "Activity Rank", pct_in_risk_zone = "% in Risk-Height Zone", risk_rank = "Risk-Height Rank")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r species-risk-stat-annex, results='asis'}
annex_note(params$xlsx_species_risk_stat)
```

```{r stat-incident-risk-context-heading, results='asis'}
if (!is.null(params$incident_risk_context_stat)) cat("#### Risk Context at Incident Turbines\n\n")
```
```{r incident-risk-context-stat-table}
if (!is.null(params$incident_risk_context_stat)) {
  report_table(
    rename_display(
      drop_cols(params$incident_risk_context_stat, c("below_median_activity", "below_median_risk_height", "low_baseline_risk_supported")),
      c(incident_id = "Incident", turbine = "Turbine", species = "Species", cluster_id = "Cluster",
        n_clusters = "N Clusters", track_activity_rank = "Activity Rank", track_pct_of_total = "% of Species Tracks",
        risk_height_rank = "Risk-Height Rank", pct_in_risk_zone = "% in Risk-Height Zone")
    ),
    max_col_width_cm = 1.5
  )
}
```

```{r stat-incident-risk-context-lead, results='asis'}
if (!is.null(params$incident_risk_context_stat)) cat("Per-incident detail:\n\n")
```

```{r incident-risk-context-stat-text, results='asis'}
if (!is.null(params$incident_risk_context_stat) && nrow(params$incident_risk_context_stat) > 0) {
  dt <- params$incident_risk_context_stat
  cat("\n")
  for (i in seq_len(nrow(dt))) {
    r <- dt[i, ]
    verdict <- if (isTRUE(r$low_baseline_risk_supported)) {
      "its cluster is below median on both metrics, so the baseline activity/exposure data do not contradict treating this cluster's risk as comparatively lower than the farm's other clusters"
    } else {
      "its cluster is not below median on both metrics, so these data do not support treating this cluster's risk as comparatively low"
    }
    cat(sprintf(
      "- **%s** (%s, %s): cluster %s ranks %s of %s by track activity (%s%% of the species' farm-wide tracks) and %s of %s by time in the risk-height zone (%s%%) -- %s.\n",
      r$incident_id, r$turbine, r$species, r$cluster_id,
      r$track_activity_rank, r$n_clusters, r$track_pct_of_total,
      r$risk_height_rank, r$n_clusters, r$pct_in_risk_zone,
      verdict
    ))
  }
  cat("\n")
}
```

# Minimum Individuals per Time Bin

Minimum number of distinct individuals per priority species detected in the same `r params$min_individuals_bin_min`-minute time bin, farm-wide (pooling tracks from every IDF unit) and summarised by day, over the full project history. Within each bin, two or more tracks of the *same* species are counted as a single individual when their positions are within `r params$min_individuals_merge_dist_m` m of each other; tracks of different species are never merged with one another.

## Summary

<!-- Source: summarise_min_individuals(min_indiv_bins_dt), R/track_min_individuals.R -->
```{r min-indiv-summary-table}
if (!is.null(params$min_indiv_summary)) {
  report_table(rename_display(
    params$min_indiv_summary,
    c(spec = "Species", n_bins = "Bins", peak_individuals = "Peak Individuals",
      peak_bin_start = "Peak Time", mean_individuals_nonzero = "Mean (Non-zero Bins)")
  ))
}
```
```{r min-indiv-summary-annex, results='asis'}
annex_note(params$xlsx_min_indiv)
```

## Daily Peak, by Species

<!-- Source: plot_daily_max_individuals(min_indiv_daily_dt, date_breaks = "1 month", geom_type = "bar"), R/track_min_individuals.R -->
```{r min-indiv-daily-plot, fig.width=6.30, fig.height=6.30}
if (!is.null(params$min_indiv_plot_daily)) print(params$min_indiv_plot_daily)
```

# Annexes

The full detail behind each table above (including all rows and columns, not only the summaries shown here) is provided as separate files in the same output folder as this report, one workbook/plot set per section: system availability, data coverage, curtailment response assessment, shutdown time, safe distance, 3D coverage, fatality investigation (full track/window detail), manual risk clusters and statistical turbine clustering (both including the cluster-threshold sensitivity sweep, weekly time series, and per-turbine/per-cluster breakdowns), and minimum individuals per bin.
