---
title: "`r params$title`"
output: word_document
params:
  title: ""
  project_ref: ""
  report_start: ""
  report_end: ""
  analysis_date: ""
  username: ""
  code_version: ""

  availability_by_idf: !r NULL
  availability_plot_cal: !r NULL
  availability_plot_freq: !r NULL
  availability_cal_report_months: !r NULL
  availability_cal_full_filename: !r NULL
  idf_availability_top_n: !r NULL

  coverage_turbine_summary: !r NULL
  coverage_idf_summary: !r NULL

  latency_by_turbine: !r NULL
  latency_bands: !r NULL
  latency_plot: !r NULL
  latency_timeline_plot: !r NULL
  latency_n_no_data: !r NULL
  latency_pct_no_data: !r NULL
  latency_n_below_cutin: !r NULL
  latency_pct_below_cutin: !r NULL

  shutdown_by_turbine: !r NULL
  shutdown_bands: !r NULL
  shutdown_plot: !r NULL

  coverage3d_by_turbine: !r NULL
  coverage3d_priority_by_turbine: !r NULL
  coverage3d_priority_class_summary: !r NULL
  coverage_cylinder_inner_radius: !r NULL

  safe_dist_overall: !r NULL
  safe_dist_by_species: !r NULL
  safe_dist_plot: !r NULL
  safe_dist_ci_overall: !r NULL
  safe_dist_ci_by_species: !r NULL
  safe_dist_by_month_plot: !r NULL
  safe_dist_trend_p_value: !r NULL
  safe_dist_trend_direction: !r NULL
  safe_dist_species_test_p_value: !r NULL
  safe_dist_species_test_method: !r NULL

  no_response_examples_plot: !r NULL
  slowest_response_examples_plot: !r NULL
  n_no_response_examples: !r NULL
  n_slowest_examples: !r NULL

  fatality_signal_counts: !r NULL
  fatality_top_candidates: !r NULL
  fatality_window_response_summary: !r NULL
  fatality_abundance_pre_post: !r NULL

  risk_cluster_map: !r NULL
  risk_cluster_summary: !r NULL
  risk_fatality_summary: !r NULL

  species_activity_manual: !r NULL
  species_risk_height_manual: !r NULL
  incident_risk_context_manual: !r NULL

  stat_cluster_map: !r NULL
  stat_cluster_summary: !r NULL
  stat_risk_summary: !r NULL

  species_activity_stat: !r NULL
  species_risk_height_stat: !r NULL
  incident_risk_context_stat: !r NULL

  idf_cluster_map: !r NULL
  idf_cluster_summary: !r NULL
  idf_risk_summary: !r NULL

  min_indiv_summary: !r NULL
  min_indiv_plot_daily: !r NULL

  n_turbines_total: !r NULL
  n_idf_total: !r NULL

  # Nomes (basename) dos xlsx de anexo -- 1 por tabela, para a frase "ver
  # anexo ...xlsx" logo apos cada tabela do relatorio.
  xlsx_availability: !r NULL
  xlsx_coverage_turbine: !r NULL
  xlsx_coverage_idf: !r NULL
  xlsx_latency: !r NULL
  xlsx_shutdown: !r NULL
  xlsx_safe_dist: !r NULL
  xlsx_coverage3d: !r NULL
  xlsx_fatality: !r NULL
  xlsx_risk_cluster_patterns: !r NULL
  xlsx_risk_critical_zone: !r NULL
  xlsx_stat_cluster_patterns: !r NULL
  xlsx_stat_critical_zone: !r NULL
  xlsx_species_risk_manual: !r NULL
  xlsx_species_risk_stat: !r NULL
  xlsx_curtailment_cluster_idf: !r NULL
  xlsx_curtailment_examples: !r NULL
  xlsx_min_indiv: !r NULL

  # Literais de configuracao (userSettings_BSH.R) usados so' para texto
  # descritivo -- cada secção que aplica um threshold/cut-off mostra o
  # VALOR concreto usado na analise, nao so' o nome do parametro.
  heartbeat_interval_min: !r NULL
  heartbeat_offline_gap_min: !r NULL

  curtailment_start_end_gap_sec: !r NULL
  curtailment_max_next_gap_sec: !r NULL
  curtailment_drop_pct_threshold: !r NULL
  safe_shutdown_rpm: !r NULL

  shutdown_time_thresholds: !r NULL
  shutdown_time_low_cut: !r NULL
  shutdown_time_high_cut: !r NULL
  shutdown_time_buffer_sec: !r NULL

  curtailment_latency_decline_pct: !r NULL
  curtailment_cutin_rpm: !r NULL
  response_timeline_unit: !r NULL

  curtailment_example_window_before_min: !r NULL
  curtailment_example_window_after_min: !r NULL

  safe_dist_reference_line_m: !r NULL
  safe_dist_rpm_threshold: !r NULL
  safe_dist_already_slowing_rpm: !r NULL

  track_proximity_threshold_m: !r NULL
  fatality_post_incident_days: !r NULL

  flight_min_track_points: !r NULL
  flight_speed_ms_min: !r NULL
  flight_speed_ms_max: !r NULL
  risk_height_lower: !r NULL
  risk_height_upper: !r NULL

  cluster_max_dist_m: !r NULL
  cluster_perm_n: !r NULL

  min_individuals_bin_min: !r NULL
  min_individuals_merge_dist_m: !r NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Tabela flextable com o estilo visual do relatorio -- mesmos helpers de
# report/monthly_report_template.rmd, portados para aqui para o relatorio
# anual seguir a mesma convencao visual (arredondamento, largura de coluna,
# renomeacao para apresentacao). round_display() corre sempre primeiro,
# aqui dentro -- nenhuma tabela do relatorio precisa de a chamar manualmente.
report_table <- function(x, caption = NULL, max_col_width_cm = NULL, col_widths_cm = NULL) {
  ft <- flextable::flextable(round_display(x)) |>
    flextable::theme_box() |>
    flextable::bg(part = "header", bg = "gray85") |>
    flextable::bold(part = "header") |>
    flextable::fontsize(size = 9, part = "header") |>
    flextable::fontsize(size = 9, part = "body") |>
    flextable::align(align = "center", part = "header") |>
    flextable::valign(valign = "center", part = "all") |>
    flextable::autofit()
  if (!is.null(max_col_width_cm)) ft <- cap_col_width(ft, max_col_width_cm)
  if (!is.null(col_widths_cm)) ft <- set_col_max_width(ft, col_widths_cm)
  if (!is.null(caption)) ft <- flextable::set_caption(ft, caption)
  ft
}

# Arredonda, so' para apresentacao no docx, cada coluna numerica que tenha
# algum valor nao-inteiro para `digits` casas decimais (2 por omissao) --
# colunas so' com valores inteiros (contagens) ficam como estao. Excecao: se
# arredondar a `digits` casas desse 0 mas o valor real nao e' zero, estende
# casas decimais ate aparecer o 1o digito significativo (ex: 0.001), para
# nao mostrar "0.00" nalgo que na realidade nao e' zero. Devolve os valores
# ja como texto formatado (sprintf) -- os exports xlsx (feitos a partir dos
# objetos originais, nao deste helper) mantêm sempre os valores tal como
# calculados pelas funcoes de analise.
round_display <- function(x, digits = 2) {
  x <- as.data.frame(x)
  for (col in names(x)) {
    v <- x[[col]]
    if (!is.numeric(v) || is.integer(v)) next
    if (all(v == round(v), na.rm = TRUE)) next
    x[[col]] <- vapply(v, function(val) {
      if (is.na(val)) return(NA_character_)
      d <- digits
      while (round(val, d) == 0 && val != 0 && d < 6) d <- d + 1
      sprintf(paste0("%.", d, "f"), val)
    }, character(1))
  }
  x
}

cap_col_width <- function(ft, max_width_cm = 2) {
  # dim() (nao flextable::dim()) -- dim.flextable e' um metodo S3 registado
  # pelo flextable no generico base dim(), nao necessariamente exportado como
  # simbolo chamavel via flextable::dim()
  widths_in <- dim(ft)$widths
  capped_cm <- pmin(widths_in * 2.54, max_width_cm)
  flextable::width(ft, j = seq_along(capped_cm), width = capped_cm, unit = "cm")
}

# Como cap_col_width(), mas por coluna -- widths_cm e' um vector nomeado
# c("Nome da Coluna" = largura_maxima_cm, ...), usando os nomes ja'
# apresentados (apos rename_display()). So' encolhe (nunca alarga) as
# colunas indicadas ate' esse maximo; colunas nao mencionadas ficam como o
# autofit() as deixou. Nomes que nao existirem na tabela sao ignorados.
set_col_max_width <- function(ft, widths_cm) {
  widths_in <- dim(ft)$widths
  idx <- match(names(widths_cm), ft$col_keys)
  hit <- !is.na(idx)
  if (any(hit)) {
    capped_cm <- pmin(widths_in[idx[hit]] * 2.54, unname(widths_cm[hit]))
    ft <- flextable::width(ft, j = idx[hit], width = capped_cm, unit = "cm")
  }
  ft
}

# Renomeia colunas so' para APRESENTACAO no docx -- os exports em xlsx
# (annexos) usam sempre os nomes tecnicos originais dos objetos R. mapping:
# c(nome_original = "Nome Legivel"); colunas nao mencionadas ficam como estao.
rename_display <- function(x, mapping) {
  x <- as.data.frame(x)
  idx <- match(names(mapping), names(x))
  hit <- !is.na(idx)
  names(x)[idx[hit]] <- unname(mapping)[hit]
  x
}

# Remove colunas da tabela apresentada no docx (o xlsx correspondente, feito
# a partir do objeto original nao filtrado, continua completo)
drop_cols <- function(x, cols) {
  x <- as.data.frame(x)
  x[, setdiff(names(x), cols), drop = FALSE]
}

# Substitui VALORES (nao nomes de coluna) de uma coluna categorica por
# rotulos legiveis
recode_values <- function(x, col, mapping) {
  x <- as.data.frame(x)
  hit <- x[[col]] %in% names(mapping)
  x[[col]][hit] <- unname(mapping[x[[col]][hit]])
  x
}

# Frase-padrao, logo apos cada tabela, a apontar para o xlsx de anexo com o
# detalhe completo (todas as linhas/colunas) -- pedido do Paulo (2026-08)
# para toda tabela do relatorio, nao so' as ja' identificadas como resumos
# reduzidos. Chamar APENAS num chunk results='asis' proprio, separado do
# chunk que desenha a tabela (report_table() depende do auto-print do
# knit_print.flextable, que so' funciona corretamente quando essa e' a
# UNICA expressao visivel do bloco -- ver nota "Cada tabela/plot..." acima).
annex_note <- function(xlsx_name) {
  if (!is.null(xlsx_name)) {
    cat(sprintf("\n*The full table is available in the accompanying workbook: `%s`.*\n", xlsx_name))
  }
}
```

<!--
Cada tabela/plot abaixo tem, imediatamente acima do chunk que a produz, um
comentario "Source: ..." a apontar para a funcao R (e ficheiro) que calcula
o objeto correspondente em IDF_analysis.R -- usar isso para encontrar
rapidamente onde ajustar cada tabela/plot sem ter de procurar pelo nome do
param em todo o script. Estes comentarios HTML nao aparecem no .docx gerado.

Cada tabela/plot tem tambem a sua propria subsecção (##), com 1 frase a
identificar o objeto, mesmo quando 2 tabelas pertencem à mesma secção -- 2
flextables em chunks consecutivos sem nenhum paragrafo de texto a
separa-los tendem a sair "coladas" no docx (dificeis de selecionar/mover/
editar independentemente no Word). Uma frase de texto entre elas garante
uma quebra de paragrafo real a separa-las (mesma correcao aplicada ao
relatorio mensal, report/monthly_report_template.rmd).

Plots com eixo de datas usam fig.width=6.30 (=16cm) por omissao, com
expand=c(0,0) e breaks mais curtos definidos a montante em R (ver
comentarios "Source:"), para nao ter datas fora do periodo coberto e para
os rotulos do eixo ficarem legiveis mesmo num historico de varios meses.
-->

**`r params$project_ref`**

Report period: `r params$report_start` to `r params$report_end`

Analysis date: `r params$analysis_date`

Responsible Team: `r params$username`

Code version: `r params$code_version`

This report is descriptive and fully automated, generated end-to-end by an R code pipeline. It presents the metrics produced by the IDF analysis pipeline over the full project history to date, without further interpretation, except where an explicit threshold (e.g. the KNE safe-distance reference line, shutdown-time bands) is already part of the pre-defined methodology.

---

# System Availability (Heartbeats)

Heartbeats are expected every `r params$heartbeat_interval_min` minutes; an IDF unit is considered offline once the gap since its last heartbeat exceeds `r params$heartbeat_offline_gap_min` minutes (at least 2 consecutive heartbeats missed). Full project history to date.

## Availability by IDF Unit

<!-- Source: idf_availability_summary$by_idf <- summarise_availability(idf_availability_dt), R/availability_daylight.R -->
```{r availability-table}
if (!is.null(params$availability_by_idf)) {
  report_table(
    rename_display(
      drop_cols(params$availability_by_idf, c("daylight_mins_total", "days_covered", "offline_mins_total", "availability_pct")),
      c(idf = "IDF Unit", monitoring_period_pct = "Offline (%)", availability_cat = "Category")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r availability-annex, results='asis'}
annex_note(params$xlsx_availability)
```

## Availability Calendar

Daily offline percentage per IDF unit, laid out as a calendar -- the `r params$idf_availability_top_n` units with the most offline time over the full project history, for the last `r params$availability_cal_report_months` months only.

<!-- Source: plot_availability_calendar(), R/availability_daylight.R -->
```{r availability-cal, fig.width=6.30, fig.height=9}
if (!is.null(params$availability_plot_cal)) print(params$availability_plot_cal + ggplot2::theme(legend.position = "bottom"))
```
```{r availability-cal-annex, results='asis'}
if (!is.null(params$availability_cal_full_filename)) {
  cat(sprintf("\n*The full calendar (every IDF unit, full project history) is available as an accompanying image: `%s`.*\n", params$availability_cal_full_filename))
}
```

## Availability Frequency

Count of IDF units per daylight-availability category.

<!-- Source: plot_availability_frequency(), R/availability_daylight.R -->
```{r availability-freq, fig.width=6.30, fig.height=3.5}
if (!is.null(params$availability_plot_freq)) print(params$availability_plot_freq)
```

# Data Coverage

Temporal overlap between Curtailments and SCADA (by turbine), and Heartbeats coverage (by IDF unit), over the full download history to date (not limited to the report period above).

## Curtailments / SCADA Overlap by Turbine

Number of days with data on each side, and the days where both overlap, per turbine.

<!-- Source: coverage_turbine_summary <- overlap_summary_by_turbine(coverage_turbine_dt, "Curtailments", "SCADA"), R/data_coverage.R -- pct_overlap_of_total (days_overlap/total_days) is computed here in the Rmd, not in R, purely for display -->
```{r coverage-turbine-prep, include=FALSE}
cov_turbine_dt <- NULL
if (!is.null(params$coverage_turbine_summary)) {
  cov_turbine_dt <- as.data.frame(params$coverage_turbine_summary)
  cov_turbine_dt$pct_overlap_of_total <- round(100 * cov_turbine_dt$days_overlap / cov_turbine_dt$total_days, 1)
}
```
```{r coverage-turbine-text, results='asis'}
if (!is.null(cov_turbine_dt) && nrow(cov_turbine_dt) > 0) {
  pct_of_farm <- ""
  if (!is.null(params$n_turbines_total) && params$n_turbines_total > 0) {
    pct_of_farm <- sprintf(" (%.0f%% of the %d turbines in the farm)", 100 * nrow(cov_turbine_dt) / params$n_turbines_total, params$n_turbines_total)
  }
  cat(sprintf(
    "%d turbine(s)%s have overlapping Curtailments/SCADA data, with %% Overlap ranging from %.1f%% to %.1f%%.\n\n",
    nrow(cov_turbine_dt), pct_of_farm,
    min(cov_turbine_dt$pct_overlap_of_total, na.rm = TRUE), max(cov_turbine_dt$pct_overlap_of_total, na.rm = TRUE)
  ))
}
```
```{r coverage-turbine-table}
if (!is.null(cov_turbine_dt)) {
  report_table(
    rename_display(
      drop_cols(cov_turbine_dt, c("pct_a_with_overlap", "pct_b_with_overlap")),
      c(turbine = "Turbine", total_days = "Total Days", days_a = "Days Curtailments",
        days_b = "Days SCADA", days_overlap = "Days Overlap", pct_overlap_of_total = "% Overlap")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r coverage-turbine-annex, results='asis'}
annex_note(params$xlsx_coverage_turbine)
```

## Heartbeats Coverage by IDF Unit

Days with heartbeat data, and days missing, per IDF unit.

<!-- Source: coverage_idf_summary <- presence_summary_by_idf(coverage_idf_dt), R/data_coverage.R -->
```{r coverage-idf-text, results='asis'}
if (!is.null(params$coverage_idf_summary) && nrow(params$coverage_idf_summary) > 0) {
  dt <- params$coverage_idf_summary
  pct_of_total <- ""
  if (!is.null(params$n_idf_total) && params$n_idf_total > 0) {
    pct_of_total <- sprintf(" (%.0f%% of the %d IDF units in the farm)", 100 * nrow(dt) / params$n_idf_total, params$n_idf_total)
  }
  cat(sprintf(
    "%d IDF unit(s)%s have heartbeat data, with %% Missing ranging from %.1f%% to %.1f%%.\n\n",
    nrow(dt), pct_of_total, min(dt$pct_missing, na.rm = TRUE), max(dt$pct_missing, na.rm = TRUE)
  ))
}
```
```{r coverage-idf-table}
if (!is.null(params$coverage_idf_summary)) {
  report_table(
    rename_display(
      params$coverage_idf_summary,
      c(idf = "IDF Unit", start = "From", end = "To", days_with_data = "Days with Data",
        total_days = "Total Days", days_missing = "Days Missing", pct_missing = "% Missing")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r coverage-idf-annex, results='asis'}
annex_note(params$xlsx_coverage_idf)
```

# Curtailment Response & Latency

Whether SCADA-recorded RPM dropped as expected in response to curtailment signals, over the full project history to date. The SCADA baseline used for each curtailment is the last RPM reading recorded at or before the signal, within `r params$curtailment_start_end_gap_sec` s of it; a reading recorded after the signal is never used for this purpose, so that the baseline cannot itself include any part of the response it is meant to measure. `r params$latency_n_no_data` curtailments (`r params$latency_pct_no_data`% of the total) have no such reading within that tolerance and are excluded from every table below, since no baseline RPM could be established for them; this reflects gaps in SCADA-RPM data availability, which vary by turbine and period (see the Response Latency by Turbine table below, and its accompanying annex, for the no-data share by turbine). A response is considered to have started once RPM has dropped by at least `r params$curtailment_latency_decline_pct * 100`% from its value at the start of the curtailment order; a turbine is considered stopped once RPM falls below `r params$safe_shutdown_rpm`. Both response latency and shutdown time below allow up to `r params$shutdown_time_buffer_sec` s past the end of the curtailment order for this to happen. Curtailments with an RPM below `r params$curtailment_cutin_rpm` (the cut-in speed, below which the turbine is not producing energy) at the start of the order are further excluded from the Response Latency and No-Response Events tables below, since there is no meaningful response to measure on a turbine that was already not operating: of the curtailments with a valid SCADA baseline, `r params$latency_n_below_cutin` (`r params$latency_pct_below_cutin`%) fall in this category over the period covered.

## Response Latency

Time from the curtailment signal to the first SCADA reading showing the decline defined above, by turbine, among curtailments at or above the cut-in speed.

<!-- Source: summarise_latency_by_turbine(latency_dt), R/curtailment_response_latency.R -->
```{r latency-turbine-table}
if (!is.null(params$latency_by_turbine)) {
  report_table(
    rename_display(
      drop_cols(params$latency_by_turbine, c(
        "n_curtailments", "n_no_data", "pct_no_data", "n_known",
        "n_below_cutin", "pct_below_cutin", "n_no_response", "pct_no_response"
      )),
      c(
        turbine = "Turbine", n_eligible = "Curtailments", n_reached = "Reached",
        pct_reached = "% Reached", mean_latency_sec = "Mean (s)", median_latency_sec = "Median (s)"
      )
    ),
    max_col_width_cm = 2
  )
}
```
```{r latency-turbine-annex, results='asis'}
annex_note(params$xlsx_latency)
```

### Response Latency Bands

Of the curtailments where a decline was detected, share with latency within each cut-off.

<!-- Source: summarise_latency_bands(latency_dt), R/curtailment_response_latency.R -->
```{r latency-bands-table}
if (!is.null(params$latency_bands)) {
  report_table(rename_display(
    params$latency_bands,
    c(cutoff_sec = "Cut-off (s)", pct_within_cutoff = "% Within Cut-off")
  ))
}
```
```{r latency-bands-annex, results='asis'}
annex_note(params$xlsx_latency)
```

### Response Latency Distribution

<!-- Source: plot_latency_histogram(latency_dt), R/curtailment_response_latency.R -->
```{r latency-plot, fig.width=6.30, fig.height=4}
if (!is.null(params$latency_plot)) print(params$latency_plot)
```

### Latency Temporal Pattern

Mean and standard deviation of response latency, among curtailments at or above the cut-in speed, aggregated by `r params$response_timeline_unit`.

<!-- Source: plot_latency_timeline(summarise_latency_timeline(latency_dt, unit = response_timeline_unit)), R/curtailment_response_timeline.R -->
```{r latency-timeline-plot, fig.width=6.30, fig.height=4.5}
if (!is.null(params$latency_timeline_plot)) print(params$latency_timeline_plot)
```

## Shutdown Time

Time from curtailment signal to reaching each RPM threshold, by turbine -- 3 thresholds evaluated: `r paste(params$shutdown_time_thresholds, collapse = ", ")` rpm. Bands below/above the agreed cut-offs are reported as-is, without further interpretation. Uses the same population as Response Latency above: curtailments with no SCADA baseline within `r params$curtailment_start_end_gap_sec` s of the signal, or already below the cut-in speed at the start of the order, are excluded (see the counts stated there).

### Time to Threshold by Turbine

<!-- Source: summarise_time_to_threshold(tt_dt), R/curtailment_shutdown_time.R -->
```{r shutdown-turbine-table}
if (!is.null(params$shutdown_by_turbine)) {
  report_table(
    rename_display(
      drop_cols(params$shutdown_by_turbine, c("median_time_sec")),
      c(
        turbine = "Turbine", threshold = "Thresh. (rpm)", n_curtailments = "Curtailments",
        n_reached = "Reached", pct_reached = "% Reached", mean_time_sec = "Mean (s)",
        sd_time_sec = "SD (s)", min_time_sec = "Min (s)", max_time_sec = "Max (s)"
      )
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r shutdown-turbine-annex, results='asis'}
annex_note(params$xlsx_shutdown)
```

### Time to Threshold Bands

A curtailment counts as "below cut" when it reached the threshold in under `r params$shutdown_time_low_cut` s (fast), and "above cut" when it took more than `r params$shutdown_time_high_cut` s (slow); cases in between count towards neither band.

<!-- Source: summarise_time_to_threshold_bands(tt_dt), R/curtailment_shutdown_time.R -->
```{r shutdown-bands-table}
if (!is.null(params$shutdown_bands)) {
  report_table(rename_display(
    params$shutdown_bands,
    stats::setNames(
      c("Thresh. (rpm)", "Reached", sprintf("%% < %ss", params$shutdown_time_low_cut), sprintf("%% > %ss", params$shutdown_time_high_cut)),
      c("threshold", "n_reached", "pct_below_cut", "pct_above_cut")
    )
  ))
}
```
```{r shutdown-bands-annex, results='asis'}
annex_note(params$xlsx_shutdown)
```

### Time to Threshold Distribution

<!-- Source: plot_time_to_threshold(), R/curtailment_shutdown_time.R -->
```{r shutdown-plot, fig.width=6.30, fig.height=6}
if (!is.null(params$shutdown_plot)) print(params$shutdown_plot)
```

## No-Response Events

A no-response event is a curtailment, at or above the cut-in speed, for which no decline of `r params$curtailment_latency_decline_pct * 100`% or more was detected within the allowance window (up to `r params$shutdown_time_buffer_sec` s past the end of the curtailment order), by turbine.

<!-- Source: summarise_latency_by_turbine(latency_dt), R/curtailment_response_latency.R -->
```{r no-response-turbine-table}
if (!is.null(params$latency_by_turbine)) {
  report_table(
    rename_display(
      drop_cols(params$latency_by_turbine, c(
        "n_curtailments", "n_no_data", "pct_no_data", "n_known",
        "n_below_cutin", "pct_below_cutin", "n_reached", "pct_reached",
        "mean_latency_sec", "median_latency_sec"
      )),
      c(
        turbine = "Turbine", n_eligible = "Curtailments",
        n_no_response = "No Response", pct_no_response = "% No Response"
      )
    ),
    max_col_width_cm = 2.5
  )
}
```
```{r no-response-turbine-annex, results='asis'}
annex_note(params$xlsx_latency)
```

```{r example-response-heading, results='asis'}
cat("## Example Response Profiles\n\n")
cat(sprintf(
  "Illustrative examples: RPM profile of individual curtailments, with the curtailment start and stop overlaid, for a window of %s minute(s) before and %s minutes after the curtailment start -- examples below are the most illustrative available (slowest: the longest latencies; no-response: the most recent), not a random or representative sample. Sections below are always shown, with the underlying counts, even when there are no examples to plot for a given category.\n\n",
  params$curtailment_example_window_before_min, params$curtailment_example_window_after_min
))
```

```{r no-response-examples-heading, results='asis'}
cat(sprintf("### No-Response Events (%s example(s))\n\n", params$n_no_response_examples))
```
<!-- Source: select_latency_examples(latency_dt, "no_response"), plot_curtailment_events_rpm(), R/curtailment_forensic_trace.R -->
```{r no-response-examples-plot, fig.width=6.30, fig.height=5.91, results='asis'}
if (!is.null(params$no_response_examples_plot)) {
  print(params$no_response_examples_plot)
} else {
  cat("No no-response events were recorded in this reporting period -- no example plot is shown.\n\n")
}
```

```{r slowest-examples-heading, results='asis'}
cat(sprintf("### Slowest Responses (%s example(s))\n\n", params$n_slowest_examples))
```
<!-- Source: select_latency_examples(latency_dt, "slowest"), plot_curtailment_events_rpm(), R/curtailment_forensic_trace.R -->
```{r slowest-examples-plot, fig.width=6.30, fig.height=5.91, results='asis'}
if (!is.null(params$slowest_response_examples_plot)) {
  print(params$slowest_response_examples_plot)
} else {
  cat("No curtailments with a detected response were available in this reporting period -- no example plot is shown.\n\n")
}
```
```{r curtailment-examples-annex, results='asis'}
annex_note(params$xlsx_curtailment_examples)
```

# Safe Distance (KNE Methodology)

Distance between the triggering track and the turbine at the moment of curtailment, compared against the KNE reference line (`r params$safe_dist_reference_line_m` m), by priority species. A turbine's estimated time-to-stop-safely uses `r params$safe_dist_rpm_threshold` rpm as the "stopped" threshold; a turbine already below `r params$safe_dist_already_slowing_rpm` rpm at the moment of the signal is treated as already slowing from a previous curtailment, not at full operating speed.

## Overall

<!-- Source: summary_safe_dist$overall <- summarise_safe_distance(safe_dist_dt, prioritysp)$overall, R/curtailment_safe_distance.R -->
```{r safe-dist-overall-table}
if (!is.null(params$safe_dist_overall)) {
  report_table(
    rename_display(
      params$safe_dist_overall,
      c(n = "N", n_ok = "OK", n_crit = "Critical", pct_ok = "% OK",
        mean_time_to_threshold_sec = "Mean React. Time (s)", mean_avg_speed_ms = "Mean Track Speed (m/s)",
        pct_already_slowing = "% Already Slowing",
        mean_min_safe_dist_m = "Mean Safe Dist. (m)", median_min_safe_dist_m = "Median Safe Dist. (m)")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r safe-dist-overall-annex, results='asis'}
annex_note(params$xlsx_safe_dist)
```

## By Species

Mean/Median Safe Dist. (m) is the reaction time to reach the RPM threshold multiplied by that track's own flight speed -- a low value can come from a fast reaction, a slow-flying bird (Mean Track Speed), or the turbine already slowing down from an earlier curtailment order at the moment this one triggered (% Already Slowing), not necessarily from this specific signal being answered unusually fast.

<!-- Source: summary_safe_dist$by_species <- summarise_safe_distance(safe_dist_dt, prioritysp)$by_species, R/curtailment_safe_distance.R -->
```{r safe-dist-species-table}
if (!is.null(params$safe_dist_by_species)) {
  report_table(
    rename_display(
      params$safe_dist_by_species,
      c(species = "Species", n = "N", n_ok = "OK", n_crit = "Critical", pct_ok = "% OK",
        mean_time_to_threshold_sec = "Mean React. Time (s)", mean_avg_speed_ms = "Mean Track Speed (m/s)",
        pct_already_slowing = "% Already Slowing",
        mean_min_safe_dist_m = "Mean Safe Dist. (m)", median_min_safe_dist_m = "Median Safe Dist. (m)")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r safe-dist-species-annex, results='asis'}
annex_note(params$xlsx_safe_dist)
```

## Distribution

<!-- Source: plot_safe_distance_hist(), R/curtailment_safe_distance.R -->
```{r safe-dist-plot, fig.width=6.30, fig.height=6}
if (!is.null(params$safe_dist_plot)) print(params$safe_dist_plot)
```

## Statistical Confidence

The tables and figure above report point percentages only. This section adds formal statistical treatment to the same underlying data: 95% confidence intervals on the % OK figures (Wilson score method, which stays reliable at small sample sizes and percentages near 0%/100%), a test for a monotonic trend in % OK over the reporting period, and a test for whether % OK differs between species by more than sampling variation would explain.

<!-- Source: summarise_safe_distance_ci(safe_dist_dt, prioritysp), R/curtailment_safe_distance.R -->
```{r safe-dist-ci-overall-table}
if (!is.null(params$safe_dist_ci_overall)) {
  report_table(rename_display(
    params$safe_dist_ci_overall,
    c(n = "N", n_ok = "OK", pct_ok = "% OK", ci_low_pct = "95% CI Low", ci_high_pct = "95% CI High")
  ))
}
```

```{r safe-dist-ci-species-table}
if (!is.null(params$safe_dist_ci_by_species) && nrow(params$safe_dist_ci_by_species) > 0) {
  report_table(rename_display(
    params$safe_dist_ci_by_species,
    c(species = "Species", n = "N", n_ok = "OK", pct_ok = "% OK", ci_low_pct = "95% CI Low", ci_high_pct = "95% CI High")
  ))
}
```

Non-overlapping confidence intervals between two species indicate a difference unlikely to be due to chance alone; overlapping intervals -- common for species with fewer curtailments, which widens the interval -- mean the data cannot distinguish them. `r if (!is.null(params$safe_dist_species_test_method) && params$safe_dist_species_test_method == "insufficient_data") "Too few species have enough curtailments this period to run a formal cross-species test." else if (!is.null(params$safe_dist_species_test_p_value)) sprintf("A formal %s test across all species with enough curtailments returned p = %.3f, i.e. a %s difference in %% OK between species at the 5%% level.", params$safe_dist_species_test_method, params$safe_dist_species_test_p_value, if (params$safe_dist_species_test_p_value < 0.05) "statistically significant" else "not statistically significant") else ""`

The figure below tracks the same % OK figure by calendar month, with its 95% confidence band, to show the trajectory over the reporting period rather than a single blended number.

<!-- Source: plot_safe_distance_by_month(summarise_safe_distance_by_month(...)), R/curtailment_safe_distance.R -->
```{r safe-dist-by-month-plot, fig.width=6.30, fig.height=4}
if (!is.null(params$safe_dist_by_month_plot)) print(params$safe_dist_by_month_plot)
```

A logistic regression of monthly outcome (OK/Crit) against calendar month tests whether this trend is `r if (!is.null(params$safe_dist_trend_direction) && params$safe_dist_trend_direction == "insufficient_data") "assessable" else "statistically significant"`. `r if (!is.null(params$safe_dist_trend_direction) && params$safe_dist_trend_direction == "insufficient_data") "The reporting period covered so far does not yet include enough distinct months with both outcomes present to fit this test reliably." else if (!is.null(params$safe_dist_trend_p_value)) sprintf("Result: %s trend, p = %.3f (%s at the 5%% level).", params$safe_dist_trend_direction, params$safe_dist_trend_p_value, if (params$safe_dist_trend_p_value < 0.05) "statistically significant" else "not statistically significant") else ""`

```{r safe-dist-stats-annex, results='asis'}
annex_note(params$xlsx_safe_dist)
```

# 3D Coverage (Topography-corrected)

Coverage of the risk airspace around each turbine, corrected for terrain, based on IDF bird track detections.

<!-- Source: summary_cov <- summarise_mesh_coverage(...), R/coverage_3d_topography.R -->
```{r coverage3d-table}
if (!is.null(params$coverage3d_by_turbine)) {
  report_table(rename_display(
    drop_cols(params$coverage3d_by_turbine, c("n_records", "n_valid", "low_sample")),
    c(wtg_id = "Turbine", n_air_mesh = "Air Mesh Cells", n_covered = "Covered Cells", pct_covered = "% Covered")
  ))
}
```

The overall figure above blends cells at every height and distance from each turbine. The table below narrows this down to the highest-priority quadrant: cells below `r params$coverage_cylinder_inner_radius` m of horizontal distance from the turbine ("inner" band) that also sit within the risk height threshold ("at risk" band) -- the combination most relevant for assessing detection capability around a collision.

```{r coverage3d-priority-table}
if (!is.null(params$coverage3d_priority_by_turbine) && nrow(params$coverage3d_priority_by_turbine) > 0) {
  report_table(rename_display(
    drop_cols(params$coverage3d_priority_by_turbine, c("risk_band", "dist_band", "coverage_class")),
    c(wtg_id = "Turbine", n_mesh = "Air Mesh Cells", n_covered = "Covered Cells", pct_covered = "% Covered")
  ))
}
```

Turbines are further grouped into two coverage classes based on that same priority-quadrant figure, to give a quick count of how many turbines fall below the 90% coverage mark.

```{r coverage3d-class-summary-table}
if (!is.null(params$coverage3d_priority_class_summary) && nrow(params$coverage3d_priority_class_summary) > 0) {
  report_table(rename_display(
    params$coverage3d_priority_class_summary,
    c(coverage_class = "Coverage", n_units = "Num. Units", pct_units = "% of Units")
  ))
}
```

```{r coverage3d-annex, results='asis'}
annex_note(params$xlsx_coverage3d)
```

Note: interactive 3D plots are saved separately as HTML files (folder `coverage_3d/`) and are not embedded in this document.

# Fatality Investigation

Investigation of the known fatality incidents (`r params$track_proximity_threshold_m` m proximity threshold to identify candidate tracks; the recorded incident date is when the carcass was found during a turbine ground survey, not the date of collision, so each incident is investigated over a window of days before that date, not the single day).

## Candidate Tracks by Signal

Count of tracks recorded near each incident's turbine, by signal type (e.g. curtailment triggered vs. not, near vs. far), for the days before each incident.

<!-- Source: fatality_summary$counts_by_signal <- summarise_fatality_tracks(fatality_tracks_dt)$counts_by_signal, R/fatality_track_investigation.R -->
```{r fatality-signal-counts-table}
if (!is.null(params$fatality_signal_counts)) {
  report_table(
    rename_display(
      params$fatality_signal_counts,
      c(incident_id = "Incident", turbine = "Turbine", species = "Species", signal = "Signal",
        n_tracks = "Tracks", pct_of_incident = "% of Incident")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r fatality-signal-counts-annex, results='asis'}
annex_note(params$xlsx_fatality)
```

## Top Candidate Tracks

The tracks most likely associated with each incident -- those whose last recorded position ends closest to the turbine, among the candidate signal types. This is an adjusted summary (Incident, Turbine, Species, Triggered Curtailment and Signal only); the full table (all candidate tracks, including track ID, point counts, distances and timestamps) is in the accompanying workbook. Triggered Curtailment records only whether any curtailment order in the log is linked to that specific track (a presence/absence check) -- it is independent of the response-latency methodology in "Curtailment Response Around Each Incident" below. A fatality can occur with no curtailment ever triggered for the responsible track, particularly when the bird is detected already close to the turbine.

<!-- Source: fatality_summary$top_candidates <- summarise_fatality_tracks(fatality_tracks_dt)$top_candidates, R/fatality_track_investigation.R -->
```{r fatality-top-candidates-table}
if (!is.null(params$fatality_top_candidates) && nrow(params$fatality_top_candidates) > 0) {
  dt <- as.data.frame(params$fatality_top_candidates)
  dt <- dt[, intersect(c("incident_id", "turbine", "species", "triggered_curtailment", "signal"), names(dt)), drop = FALSE]
  report_table(rename_display(
    dt,
    c(incident_id = "Incident", turbine = "Turbine", species = "Species",
      triggered_curtailment = "Triggered Curtailment", signal = "Signal")
  ))
}
```
```{r fatality-top-candidates-empty, results='asis'}
if (!is.null(params$fatality_top_candidates) && nrow(params$fatality_top_candidates) == 0) {
  cat("No candidate tracks meeting the analysis requirements (signal type and proximity window, see Candidate Tracks by Signal above) were found for the known incidents.\n\n")
}
```
```{r fatality-top-candidates-annex, results='asis'}
annex_note(params$xlsx_fatality)
```

## Curtailment Response Around Each Incident

Response latency and no-response events (same definitions as the farm-wide "Curtailment Response & Latency" section, R/curtailment_response_latency.R) restricted to each incident's turbine and window of days before the incident. This covers every curtailment recorded at that turbine during the window, from any track, not only the candidate track(s) identified in "Top Candidate Tracks" above -- a track with no associated curtailment there (Triggered Curtailment = False) is not represented in the Curtailments count here, and a low or zero No Response figure reflects only the curtailments that did occur during the window, not necessarily a response to that specific candidate. Curtailments without a SCADA baseline within `r params$curtailment_start_end_gap_sec` s before the signal are reported separately (No Data) rather than excluded outright -- with few curtailments per incident, an unassessed one is proportionally more significant here than in the farm-wide tables above.

<!-- Source: fatality_window_response_summary_dt <- rbindlist over fatality_windows[[id]]$curtailment_response$summary, R/fatality_window_analysis.R -->
```{r fatality-window-response-empty, results='asis'}
# fatality_windows[[id]]$curtailment_response$summary sempre devolve 1 linha
# por incidente (mesmo sem NENHUM curtailment na janela, ver
# summarise_latency() -- R/curtailment_response_latency.R), por isso a
# tabela abaixo nunca fica genuinamente vazia (0 linhas); quando NENHUM
# incidente teve curtailments na sua janela, fica so com "Incident" e
# zeros/NA em todas as outras colunas, o que e' informativo mas pode
# parecer uma tabela "vazia" -- esta nota explica o padrao antes da tabela.
if (!is.null(params$fatality_window_response_summary) && nrow(params$fatality_window_response_summary) > 0 &&
    all(params$fatality_window_response_summary$n_curtailments == 0)) {
  cat("No curtailments were recorded at any incident turbine during its analysis window, so no response-latency figures could be computed for this section (Curtailments = 0 for every incident below).\n\n")
}
```
```{r fatality-window-response-table}
if (!is.null(params$fatality_window_response_summary) && nrow(params$fatality_window_response_summary) > 0) {
  report_table(
    rename_display(
      drop_cols(params$fatality_window_response_summary, c("n_curtailments", "n_known", "n_below_cutin", "pct_below_cutin")),
      c(
        incident_id = "Incident", n_no_data = "No Data", pct_no_data = "% No Data",
        n_eligible = "Curtailments", n_reached = "Reached",
        pct_reached = "% Reached", n_no_response = "No Response", pct_no_response = "% No Response",
        mean_latency_sec = "Mean (s)", median_latency_sec = "Median (s)"
      )
    ),
    max_col_width_cm = 2
  )
}
```
```{r fatality-window-response-annex, results='asis'}
annex_note(params$xlsx_fatality)
```

## Abundance Before/After Each Incident

Minimum-individuals abundance of the incident's species, comparing the `r params$fatality_post_incident_days`-day window after the incident date against the days-before window used for the track investigation above -- descriptive only, a difference may reflect the incident or simply the natural phenology of the migration passing through, no causality is assumed.

<!-- Source: fatality_abundance_pre_post_dt <- rbindlist over fatality_windows[[id]]$abundance <- summarise_individuals_pre_post(), R/fatality_window_analysis.R -->
```{r fatality-abundance-table}
if (!is.null(params$fatality_abundance_pre_post)) {
  report_table(
    rename_display(
      drop_cols(params$fatality_abundance_pre_post, "mean_individuals"),
      c(incident_id = "Incident", period = "Period", n_days = "Days", n_bins = "Bins",
        peak_individuals = "Peak Individuals")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r fatality-abundance-annex, results='asis'}
annex_note(params$xlsx_fatality)
```

```{r cluster-section-guards, include=FALSE}
# Secção 8 combina a via manual (antigas 7.5-7.8), a via estatistica
# (antiga secção 8 standalone) e a via por unidade IDF partilhada (2026-08)
# num so' capitulo, cada uma na sua propria subsecção -- cada uma so'
# aparece (titulo incluido) quando tem conteudo: manual liga/desliga com
# run_sections$risk_clusters, estatistica com run_sections$turbine_clustering
# (ambas em userSettings_BSH.R), IDF com o mesmo run_sections$risk_clusters
# da via manual (ver run_idf, IDF_analysis.R secção 10 -- nao e' um switch
# novo).
show_manual_cluster <- !is.null(params$risk_cluster_map) || !is.null(params$risk_cluster_summary) || !is.null(params$risk_fatality_summary) || !is.null(params$species_activity_manual)
show_stat_cluster    <- !is.null(params$stat_cluster_map) || !is.null(params$stat_cluster_summary) || !is.null(params$stat_risk_summary) || !is.null(params$species_activity_stat)
show_idf_cluster     <- !is.null(params$idf_cluster_map) || !is.null(params$idf_cluster_summary) || !is.null(params$idf_risk_summary)
```

```{r cluster-section-heading, results='asis'}
if (show_manual_cluster || show_stat_cluster || show_idf_cluster) {
  cat("# Turbine Clustering & Risk by Sector\n\n")
  cat("Turbines grouped into clusters, up to 3 independent methods: manual sectors (pre-defined, `manual_turbine_clusters`), statistical clusters (grouped by distance, max ", params$cluster_max_dist_m, " m between turbines in the same cluster), and IDF-unit groups (turbines sharing the same Primary IDF unit, from the turbine/IDF coverage matrix). Each method groups the same underlying curtailment and track data differently; for each, curtailments per cluster and a permutation-test-based risk summary at the incident turbines (species activity/risk-height exposure by cluster, for the fatality-incident species, is computed for the manual and statistical clusters only -- rank + permutation test, ", params$cluster_perm_n, " permutations where applicable).\n\n", sep = "")
}
```

```{r manual-cluster-heading, results='asis'}
if (show_manual_cluster) cat("## Manual Clustering\n\n")
```

```{r manual-cluster-map-heading, results='asis'}
if (!is.null(params$risk_cluster_map)) cat("### Manual Risk Clusters Map\n\nTurbine sectors as defined manually (`manual_turbine_clusters`), with the incident turbines highlighted.\n\n")
```
<!-- Source: p_map_manual <- plot_turbine_clusters_map(wtg, cluster_dt_manual, ...), R/turbine_spatial_clusters.R -->
```{r risk-cluster-map, fig.width=6.30, fig.height=5.04}
if (!is.null(params$risk_cluster_map)) print(params$risk_cluster_map)
```

```{r manual-cluster-summary-heading, results='asis'}
if (!is.null(params$risk_cluster_summary)) cat("### Curtailments by Manual Sector\n\nTotal curtailments per manual sector, over the full project history.\n\n")
```
<!-- Source: cluster_summary_manual$by_cluster <- summarise_cluster_curtailments(curtl_cl_manual_dt)$by_cluster, R/curtailment_cluster_patterns.R -->
```{r risk-cluster-summary-table}
if (!is.null(params$risk_cluster_summary)) {
  report_table(rename_display(
    params$risk_cluster_summary,
    c(cluster_id = "Sector", n_turbines = "Turbines", n_total = "Curtailments",
      mean_per_turbine = "Mean per Turbine", cluster_rank = "Rank")
  ))
}
```
```{r risk-cluster-summary-annex, results='asis'}
annex_note(params$xlsx_risk_cluster_patterns)
```

```{r manual-risk-summary-heading, results='asis'}
if (!is.null(params$risk_fatality_summary)) cat("### Risk Summary at Incident Turbines\n\nOne row per known fatality incident: its turbine's share of its manual sector's curtailments (Sector Curtlms.), and its rank among the sector's turbines by that share (Curtlm. Rank). Two incidents at the same turbine share the same sector figures.\n\n")
```
<!-- Source: fatality_risk_summary_dt <- merge(fatality_incidents, critical_zone_manual_dt, perm_manual_dt), IDF_analysis.R section 10.3 (critical_zone_manual_dt from summarise_turbine_critical_zone(), R/turbine_critical_zone_summary.R; perm_manual_dt from permutation_test_marginal_contribution_all(), R/curtailment_cluster_patterns.R) -->
```{r risk-fatality-summary-table}
if (!is.null(params$risk_fatality_summary)) {
  dt <- as.data.frame(params$risk_fatality_summary)
  dt <- dt[, intersect(c("incident_id", "turbine", "n_total", "cluster_rank"), names(dt)), drop = FALSE]
  report_table(rename_display(
    dt,
    c(incident_id = "Incident", turbine = "Turbine", n_total = "Sector Curtlms.", cluster_rank = "Curtlm. Rank")
  ))
}
```
```{r risk-fatality-summary-annex, results='asis'}
annex_note(params$xlsx_risk_critical_zone)
```

```{r manual-species-risk-heading, results='asis'}
if (!is.null(params$species_activity_manual) && !is.null(params$species_risk_height_manual)) {
  cat("### Species Activity & Risk-Height Exposure by Cluster\n\n")
  cat(sprintf(
    "Complementary view, independent of curtailments: for the species involved in the known fatality incidents, farm-wide track activity and flight-height risk exposure, by manual sector, over the full project history. Track activity is the number of distinct tracks of that species whose closest-approach turbine falls in that sector; risk-height exposure is the %% of that species' reliable flight-height readings (tracks with at least %s points and a flight speed between %s and %s m/s, in that sector) that fall within the %s-%s m rotor-swept band. Both are ranked per species (rank 1 = highest); a sector ranking high on both is where this species is both most frequently present and most often flying at rotor height, relative to the other sectors -- not a measure of curtailment response or turbine performance.\n\n",
    params$flight_min_track_points, params$flight_speed_ms_min, params$flight_speed_ms_max,
    params$risk_height_lower, params$risk_height_upper
  ))
}
```
<!-- Source: species_activity_manual_dt <- summarise_species_cluster_activity(), species_risk_height_manual_dt <- summarise_species_cluster_risk_height(), R/species_cluster_risk_ranking.R -->
```{r species-risk-manual-table}
if (!is.null(params$species_activity_manual) && !is.null(params$species_risk_height_manual)) {
  dt <- merge(
    as.data.frame(params$species_activity_manual),
    as.data.frame(params$species_risk_height_manual),
    by = c("spec", "cluster_id"), all = TRUE
  )
  dt <- dt[, intersect(c(
    "spec", "cluster_id", "n_tracks", "pct_of_total", "activity_rank",
    "pct_in_risk_zone", "risk_rank"
  ), names(dt)), drop = FALSE]
  dt <- dt[order(dt$spec, dt$activity_rank), ]
  report_table(
    rename_display(
      dt,
      c(spec = "Species", cluster_id = "Sector", n_tracks = "Tracks", pct_of_total = "% of Species Tracks",
        activity_rank = "Activity Rank", pct_in_risk_zone = "% in Risk-Height Zone", risk_rank = "Risk-Height Rank")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r species-risk-manual-annex, results='asis'}
annex_note(params$xlsx_species_risk_manual)
```

```{r manual-incident-risk-context-heading, results='asis'}
if (!is.null(params$incident_risk_context_manual)) cat("#### Risk Context at Incident Turbines\n\nFor each incident's turbine, where its sector falls in the two rankings above -- \"below median\" means that sector ranks in the lower half of sectors for that species on that metric (comparatively less active / less exposed than most other sectors, for that species). This describes relative standing only, using the full project history; it does not establish causality with the incident, and being below median on both metrics does not amount to a validated \"low risk\" threshold -- it only means the baseline activity/exposure data do not contradict treating that sector's risk as comparatively lower than the farm's other sectors.\n\n")
```
<!-- Source: incident_risk_context_manual_dt <- summarise_incident_cluster_risk_context(), R/species_cluster_risk_ranking.R -->
```{r incident-risk-context-manual-table}
if (!is.null(params$incident_risk_context_manual)) {
  report_table(
    rename_display(
      drop_cols(params$incident_risk_context_manual, c("below_median_activity", "below_median_risk_height", "low_baseline_risk_supported")),
      c(incident_id = "Incident", turbine = "Turbine", species = "Species", cluster_id = "Sector",
        n_clusters = "N Sectors", track_activity_rank = "Activity Rank", track_pct_of_total = "% of Species Tracks",
        risk_height_rank = "Risk-Height Rank", pct_in_risk_zone = "% in Risk-Height Zone")
    ),
    max_col_width_cm = 1.5
  )
}
```

```{r manual-incident-risk-context-lead, results='asis'}
if (!is.null(params$incident_risk_context_manual)) cat("Per-incident detail:\n\n")
```

```{r incident-risk-context-manual-text, results='asis'}
if (!is.null(params$incident_risk_context_manual) && nrow(params$incident_risk_context_manual) > 0) {
  dt <- params$incident_risk_context_manual
  cat("\n")
  for (i in seq_len(nrow(dt))) {
    r <- dt[i, ]
    # NA (nao FALSE) quando a especie do incidente nao tem NENHUM track
    # farm-wide que passe os filtros de summarise_species_cluster_activity()/
    # summarise_species_cluster_risk_height() (R/species_cluster_risk_ranking.R)
    # -- ex: uma especie nunca detetada pelo sistema IDF, so' confirmada por
    # observacao humana no achado da carcaca. Sem este caso a parte "else"
    # abaixo lia-se como "confirmamos que nao esta' abaixo da mediana", o que
    # e' FALSO quando na realidade nao houve dados nenhuns para avaliar.
    if (is.na(r$track_activity_rank) || is.na(r$risk_height_rank)) {
      cat(sprintf(
        "- **%s** (%s, %s): sector %s -- no farm-wide track of this species meeting the analysis requirements was found, so no activity/risk-height ranking could be computed for its sector (the species may not have been detected by the IDF system at all).\n",
        r$incident_id, r$turbine, r$species, r$cluster_id
      ))
    } else {
      verdict <- if (isTRUE(r$low_baseline_risk_supported)) {
        "its sector is below median on both metrics, so the baseline activity/exposure data do not contradict treating this sector's risk as comparatively lower than the farm's other sectors"
      } else {
        "its sector is not below median on both metrics, so these data do not support treating this sector's risk as comparatively low"
      }
      cat(sprintf(
        "- **%s** (%s, %s): sector %s ranks %s of %s by track activity (%s%% of the species' farm-wide tracks) and %s of %s by time in the risk-height zone (%s%%) -- %s.\n",
        r$incident_id, r$turbine, r$species, r$cluster_id,
        r$track_activity_rank, r$n_clusters, r$track_pct_of_total,
        r$risk_height_rank, r$n_clusters, r$pct_in_risk_zone,
        verdict
      ))
    }
  }
  cat("\n")
}
```
```{r incident-risk-context-manual-annex, results='asis'}
annex_note(params$xlsx_species_risk_manual)
```

```{r stat-cluster-heading, results='asis'}
if (show_stat_cluster) cat("## Statistical Clustering\n\n")
```

```{r stat-cluster-map-heading, results='asis'}
if (!is.null(params$stat_cluster_map)) cat("### Statistical Clusters Map\n\n")
```
<!-- Source: p_map_stat <- plot_turbine_clusters_map(wtg, cluster_dt_stat, ...), R/turbine_spatial_clusters.R -->
```{r stat-cluster-map, fig.width=6.30, fig.height=5.04}
if (!is.null(params$stat_cluster_map)) print(params$stat_cluster_map)
```

```{r stat-cluster-summary-heading, results='asis'}
if (!is.null(params$stat_cluster_summary)) cat("### Curtailments by Statistical Cluster\n\n")
```
<!-- Source: cluster_summary_stat$by_cluster <- summarise_cluster_curtailments(curtl_cl_stat_dt)$by_cluster, R/curtailment_cluster_patterns.R -->
```{r stat-cluster-summary-table}
if (!is.null(params$stat_cluster_summary)) {
  report_table(rename_display(
    params$stat_cluster_summary,
    c(cluster_id = "Cluster", n_turbines = "Turbines", n_total = "Curtailments",
      mean_per_turbine = "Mean per Turbine", cluster_rank = "Rank")
  ))
}
```
```{r stat-cluster-summary-annex, results='asis'}
annex_note(params$xlsx_stat_cluster_patterns)
```

```{r stat-risk-summary-heading, results='asis'}
if (!is.null(params$stat_risk_summary)) {
  cat("### Risk Summary at Incident Turbines\n\n")
  cat("Same combined view as the manual sectors section above, computed instead over the statistical clusters.\n\n")
}
```
<!-- Source: stat_risk_summary_dt <- merge(fatality_incidents, critical_zone_stat_dt, perm_stat_dt), IDF_analysis.R section 10.3 -->
```{r stat-risk-summary-table}
if (!is.null(params$stat_risk_summary)) {
  dt <- as.data.frame(params$stat_risk_summary)
  dt <- dt[, intersect(c(
    "incident_id", "turbine", "cluster_id", "n_total", "pct_of_cluster", "cluster_rank",
    "track_pct_of_total", "track_cluster_rank", "observed_pct"
  ), names(dt)), drop = FALSE]
  report_table(
    rename_display(
      dt,
      c(incident_id = "Incident", turbine = "Turbine", cluster_id = "Cluster", n_total = "Cluster Curtailments",
        pct_of_cluster = "% of Cluster", cluster_rank = "Curtailment Rank",
        track_pct_of_total = "% of Cluster Tracks", track_cluster_rank = "Track Rank",
        observed_pct = "Observed %")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r stat-risk-summary-annex, results='asis'}
annex_note(params$xlsx_stat_critical_zone)
```

```{r stat-species-risk-heading, results='asis'}
if (!is.null(params$species_activity_stat) && !is.null(params$species_risk_height_stat)) {
  cat("### Species Activity & Risk-Height Exposure by Cluster\n\n")
  cat(sprintf(
    "Same complementary view as the manual sectors section above, computed instead over the statistical clusters: farm-wide track activity and flight-height risk exposure, for the species involved in the known fatality incidents, over the full project history (tracks with at least %s points and a flight speed between %s and %s m/s; risk-height band %s-%s m).\n\n",
    params$flight_min_track_points, params$flight_speed_ms_min, params$flight_speed_ms_max,
    params$risk_height_lower, params$risk_height_upper
  ))
}
```
```{r species-risk-stat-table}
if (!is.null(params$species_activity_stat) && !is.null(params$species_risk_height_stat)) {
  dt <- merge(
    as.data.frame(params$species_activity_stat),
    as.data.frame(params$species_risk_height_stat),
    by = c("spec", "cluster_id"), all = TRUE
  )
  dt <- dt[, intersect(c(
    "spec", "cluster_id", "n_tracks", "pct_of_total", "activity_rank",
    "pct_in_risk_zone", "risk_rank"
  ), names(dt)), drop = FALSE]
  dt <- dt[order(dt$spec, dt$activity_rank), ]
  report_table(
    rename_display(
      dt,
      c(spec = "Species", cluster_id = "Cluster", n_tracks = "Tracks", pct_of_total = "% of Species Tracks",
        activity_rank = "Activity Rank", pct_in_risk_zone = "% in Risk-Height Zone", risk_rank = "Risk-Height Rank")
    ),
    max_col_width_cm = 1.5
  )
}
```
```{r species-risk-stat-annex, results='asis'}
annex_note(params$xlsx_species_risk_stat)
```

```{r stat-incident-risk-context-heading, results='asis'}
if (!is.null(params$incident_risk_context_stat)) cat("#### Risk Context at Incident Turbines\n\n")
```
```{r incident-risk-context-stat-table}
if (!is.null(params$incident_risk_context_stat)) {
  report_table(
    rename_display(
      drop_cols(params$incident_risk_context_stat, c("below_median_activity", "below_median_risk_height", "low_baseline_risk_supported")),
      c(incident_id = "Incident", turbine = "Turbine", species = "Species", cluster_id = "Cluster",
        n_clusters = "N Clusters", track_activity_rank = "Activity Rank", track_pct_of_total = "% of Species Tracks",
        risk_height_rank = "Risk-Height Rank", pct_in_risk_zone = "% in Risk-Height Zone")
    ),
    max_col_width_cm = 1.5
  )
}
```

```{r stat-incident-risk-context-lead, results='asis'}
if (!is.null(params$incident_risk_context_stat)) cat("Per-incident detail:\n\n")
```

```{r incident-risk-context-stat-text, results='asis'}
if (!is.null(params$incident_risk_context_stat) && nrow(params$incident_risk_context_stat) > 0) {
  dt <- params$incident_risk_context_stat
  cat("\n")
  for (i in seq_len(nrow(dt))) {
    r <- dt[i, ]
    # mesma razao de incident-risk-context-manual-text acima -- NA (nao
    # FALSE) quando a especie do incidente nao tem NENHUM track farm-wide
    # valido, distinto de "confirmamos que nao esta' abaixo da mediana"
    if (is.na(r$track_activity_rank) || is.na(r$risk_height_rank)) {
      cat(sprintf(
        "- **%s** (%s, %s): cluster %s -- no farm-wide track of this species meeting the analysis requirements was found, so no activity/risk-height ranking could be computed for its cluster (the species may not have been detected by the IDF system at all).\n",
        r$incident_id, r$turbine, r$species, r$cluster_id
      ))
    } else {
      verdict <- if (isTRUE(r$low_baseline_risk_supported)) {
        "its cluster is below median on both metrics, so the baseline activity/exposure data do not contradict treating this cluster's risk as comparatively lower than the farm's other clusters"
      } else {
        "its cluster is not below median on both metrics, so these data do not support treating this cluster's risk as comparatively low"
      }
      cat(sprintf(
        "- **%s** (%s, %s): cluster %s ranks %s of %s by track activity (%s%% of the species' farm-wide tracks) and %s of %s by time in the risk-height zone (%s%%) -- %s.\n",
        r$incident_id, r$turbine, r$species, r$cluster_id,
        r$track_activity_rank, r$n_clusters, r$track_pct_of_total,
        r$risk_height_rank, r$n_clusters, r$pct_in_risk_zone,
        verdict
      ))
    }
  }
  cat("\n")
}
```
```{r incident-risk-context-stat-annex, results='asis'}
annex_note(params$xlsx_species_risk_stat)
```

```{r idf-cluster-heading, results='asis'}
if (show_idf_cluster) {
  cat("## IDF Unit Grouping\n\n")
  cat("Turbines grouped by shared Primary IDF unit (turbine/IDF coverage matrix) instead of geographic sector or distance -- curtailment activity is tied to IDF/SCADA presence, not geography, so this is the most direct comparison group where IDF coverage is partial (a turbine outside the range of every IDF unit has no group here at all, and is reported as such rather than compared against an unrelated geographic sector).\n\n")
}
```

```{r idf-cluster-map-heading, results='asis'}
if (!is.null(params$idf_cluster_map)) cat("### IDF Unit Map\n\nTurbine groups as defined by shared Primary IDF unit, with the incident turbines highlighted. A turbine with no Primary IDF assigned falls outside the range of every IDF unit and has no group (shown as \"(no cluster)\").\n\n")
```
<!-- Source: p_map_idf <- plot_turbine_clusters_map(wtg, cluster_dt_idf, ...), R/turbine_spatial_clusters.R -->
```{r idf-cluster-map, fig.width=6.30, fig.height=5.04}
if (!is.null(params$idf_cluster_map)) print(params$idf_cluster_map)
```

```{r idf-cluster-summary-heading, results='asis'}
if (!is.null(params$idf_cluster_summary)) cat("### Curtailments by IDF Unit\n\nTotal curtailments per IDF unit, over the full project history.\n\n")
```
<!-- Source: cluster_summary_idf$by_cluster <- summarise_cluster_curtailments(curtl_cl_idf_dt)$by_cluster, R/curtailment_cluster_patterns.R -->
```{r idf-cluster-summary-table}
if (!is.null(params$idf_cluster_summary)) {
  report_table(rename_display(
    params$idf_cluster_summary,
    c(cluster_id = "IDF Unit", n_turbines = "Turbines", n_total = "Curtailments",
      mean_per_turbine = "Mean per Turbine", cluster_rank = "Rank")
  ))
}
```
```{r idf-cluster-summary-annex, results='asis'}
annex_note(params$xlsx_curtailment_cluster_idf)
```

```{r idf-risk-summary-heading, results='asis'}
if (!is.null(params$idf_risk_summary)) cat("### Risk Summary at Incident Turbines\n\nOne row per known fatality incident: its turbine's share of curtailments among turbines sharing the same Primary IDF unit (IDF Curtlms.), and its rank among those turbines by that share (Curtlm. Rank). An incident turbine with no Primary IDF assigned (outside the range of every IDF unit) shows no group and no ranking below -- this reflects the real absence of IDF/curtailment coverage at that turbine, not a computation error.\n\n")
```
<!-- Source: idf_risk_summary_dt <- merge(fatality_incidents, marginal_idf_dt, perm_idf_dt), IDF_analysis.R section 10.3 (marginal_idf_dt from summarise_turbine_marginal_contribution(), perm_idf_dt from permutation_test_marginal_contribution_all(), both R/curtailment_cluster_patterns.R, grouped by cluster_dt_idf) -->
```{r idf-risk-summary-table}
if (!is.null(params$idf_risk_summary)) {
  dt <- as.data.frame(params$idf_risk_summary)
  dt <- dt[, intersect(c("incident_id", "turbine", "cluster_id", "n_total", "cluster_rank"), names(dt)), drop = FALSE]
  report_table(rename_display(
    dt,
    c(incident_id = "Incident", turbine = "Turbine", cluster_id = "IDF Unit",
      n_total = "IDF Curtlms.", cluster_rank = "Curtlm. Rank")
  ))
}
```
```{r idf-risk-summary-annex, results='asis'}
annex_note(params$xlsx_curtailment_cluster_idf)
```

# Minimum Individuals per Time Bin

Minimum number of distinct individuals per priority species detected in the same `r params$min_individuals_bin_min`-minute time bin, farm-wide (pooling tracks from every IDF unit) and summarised by day, over the full project history. Within each bin, two or more tracks of the *same* species are counted as a single individual when their positions are within `r params$min_individuals_merge_dist_m` m of each other; tracks of different species are never merged with one another.

## Summary

<!-- Source: summarise_min_individuals(min_indiv_bins_dt), R/track_min_individuals.R -->
```{r min-indiv-summary-table}
if (!is.null(params$min_indiv_summary)) {
  report_table(rename_display(
    params$min_indiv_summary,
    c(spec = "Species", n_bins = "Bins", peak_individuals = "Peak Individuals",
      peak_bin_start = "Peak Time", mean_individuals_nonzero = "Mean (Non-zero Bins)")
  ))
}
```
```{r min-indiv-summary-annex, results='asis'}
annex_note(params$xlsx_min_indiv)
```

## Daily Peak, by Species

<!-- Source: plot_daily_max_individuals(min_indiv_daily_dt, species_sel = setdiff(prioritysp, "Protected"), date_breaks = "1 month", geom_type = "bar"), R/track_min_individuals.R -->
```{r min-indiv-daily-plot, fig.width=6.30, fig.height=8.66}
if (!is.null(params$min_indiv_plot_daily)) print(params$min_indiv_plot_daily)
```

# Annexes

The full detail behind each table above (including all rows and columns, not only the summaries shown here) is provided as separate files in the same output folder as this report, one workbook/plot set per section: system availability, data coverage, curtailment response assessment, shutdown time, safe distance, 3D coverage, fatality investigation (full track/window detail), manual risk clusters and statistical turbine clustering (both including the cluster-threshold sensitivity sweep, weekly time series, and per-turbine/per-cluster breakdowns), and minimum individuals per bin.
