---
title: "`r params$title`"
output: word_document
params:
  title: ""
  project_ref: ""
  script_version: ""
  start_date: ""
  end_date: ""
  analysis_date: ""
  username: ""
  
  num_IDF: ""
  num_WTG: ""
  total_wtg_covered: ""
  prop_wtg_covered: ""
  riskHeight_upper: ""
  riskHeight_lower: ""
  idf_op_detection_range: ""
  shorttrack_min_points: ""
  shorttrack_eval_range: ""
  safe_shutdown_threshold: ""
  turbinas_scada: ""
  
  ID_transitions_table: !r data.frame()
  ID_entropy_table: !r data.frame()
  ID_transition_graph: ""
  
  curtail_spatial_graph: ""
  curtail_sp_table: !r data.frame()
  curtail_stats_table: !r data.frame()
  curtail_missed_table: ""
  missed_events_table: ""
    
  short_track_curtail_table: !r data.frame()
  short_track_curtail_priority_table: !r data.frame()
  
  curtail_ID_transitions_table: !r data.frame()
  response_time_table: !r data.frame()
  shutdown_time_graph: ""
  shutdown_time_table: ""
  shutdown_time_distrib: ""
  
  delayed_curtail_graph: ""
  delayed_curtail_per_priority_graph: ""
  delayed_curtail_per_priority_prop_graph: ""
  
  safe_dist_graph: ""
  safe_dist_per_priority_graph: ""
  
  coverage_wf_graph: ""
  IDF_coverage_WF_table: ""
  coverage_per_turbine_wider_graph: ""
  coverage_per_turbine_wider_spatial_graph: ""
  coverage_per_turbine_inner_graph: ""
  coverage_per_turbine_inner_spatial_graph: ""
  
  flight_height_per_sp_graph: ""
  flight_risk_table: !r data.frame()
  flight_risk_per_sp_table: !r data.frame()
  flight_height_sp_table: !r data.frame()
  flight_speed_sp_table: !r data.frame()
---

```{r setup, include=FALSE}

   report_table <- function(x) {
    flextable::flextable(x) |>
      flextable::theme_box() |>
      flextable::bg(part = "header", bg = "gray85") |>
      flextable::bold(part = "header") |>
      flextable::fontsize(size = 9, part = "header") |>
      flextable::fontsize(size = 9, part = "body") |>
      flextable::align(align = "center", part = "header") |>
      flextable::valign(valign = "center", part = "all") |>
      flextable::autofit()
  }
```




This report was automatically generated by the R script `r params$script_version` and covers the period from `r params$start_date` to `r params$end_date` (analysis undertaken at `r params$analysis_date`).


WF, IDF and analysis parameters summary:

|Parameter | Value |
|---|---:|
|Total number of IDFs | `r params$num_IDF`|
|Total turbines | `r params$num_WTG`|
|Total number of WTGs covered | `r params$total_wtg_covered`/`r params$num_WTG` (`r params$prop_wtg_covered`%)|
|Risk-zone considered in the analyses [^1] | `r params$riskHeight_lower`-`r params$riskHeight_upper`|
|Safe shutdown operational threshold considered in the analyses [^2] | <`r params$safe_shutdown_threshold` rpm|

[^1] risk-zone was derived from turbine specifications (ranging from hub height − blade length to hub height + blade length) and rounded to the nearest 50 m interval; [^2] this threshold was adopted only as an operational indicator for the analyses.

# 1. ID Performance

## False positive/False negative analysis
Analysis not available for the current report.


## ID transitions

**Transition rate**

A transition in identification refers to changes in the species assigned at consecutive positions within the same recorded track. This analysis shows the stability of the classification algorithm.

```{r echo=FALSE}
report_table(params$ID_transitions_table)
```

```{r echo=FALSE, out.width='80%'}
knitr::include_graphics(params$ID_transition_graph)
```

**ID Entropy (Shannon Index)**

ID entropy assesses the degree of classification variation within each track:

H=0 indicate stable track identification (all frames classified as the same species),

H>0 indicate ID transitions; higher values indicate higher entropy (i.e. more transitions).

```{r echo=FALSE}
report_table(params$ID_entropy_table)
```



# 2. Efficacy
Efficacy is evaluated as the degree to which the IDF system achieved the goal of guaranteeing the pre-defined mortality threshold set for Priority Bird species.

**Risk-Normalised Fatality Rate**

Analysis not available for the current report.

**Risk per 1,000 risk-tracks**

Analysis not available for the current report.




# 3. Efficiency

## Curtailments
Total number of curtailments:
```{r echo=FALSE}
report_table(params$curtail_stats_table)
```

Number and proportion of curtailments per priority bird species:
```{r echo=FALSE}
report_table(params$curtail_sp_table)
```

Total number of curtailments per WTG (colour and size both indicate total number of curtailments per WTG; no correction or standardization has been applied to account for differences in turbine operational time):
```{r echo=FALSE, out.width='120%'}
knitr::include_graphics(params$curtail_spatial_graph)
```

### Short-tracks curtailments
Short-tracks curtailments are those due to tracks with `r params$shorttrack_min_points` or fewer positions and at a short distance (`r params$shorttrack_eval_range` m).

Total short-track curtailments (Priority Bird species pooled):
```{r echo=FALSE}
report_table(params$short_track_curtail_table)
```

Short-track curtailments per Priority Bird species:
```{r echo=FALSE}
report_table(params$short_track_curtail_priority_table)
```


### Curtailments due to ID transitions
Curtailments due to transitions are those whose tracks originated curtailment but later transited from a priority to non-priority bird ID classification (P→NP ID transition). These transitions allow assessment of potentially unnecessary curtailments.

Total number of curtailments due to ID transitions (Priority Bird species pooled):
```{r echo=FALSE}
report_table(params$curtail_ID_transitions_table)
```


### Response time
Time response is measured as the latency period, measured in seconds, between the IDF-triggered curtailment signal (“start”) and the moment when a measurable reaction from the turbine occurs, expressed as a 10% drop in rotor rotational speed (an average rotor speed before the curtailment signal is used as baseline). Only a set of turbine was included in this analysis (turbines: `r params$turbinas_scada`).

Turbine response time:
```{r echo=FALSE}
report_table(params$response_time_table)
```


### Shutdown time
Shutdown time is assessed as the time taken since curtailment trigger and rotor reaches the "safe shutdown threshold" (`r params$safe_shutdown_threshold` rpm). This classification used does not imply that the turbine was unable to stop within safe time. Only a set of turbine was included in this analysis (see "Response time" section).

Turbine shutdown classes: Very short (0-5s), Short (5-15s), Moderate (15-30s), Long (30-60s), Long (>60s):
```{r echo=FALSE, out.width='90%'}
knitr::include_graphics(params$shutdown_time_graph)
```

Number of curtailments per shutdown class:
```{r echo=FALSE}
report_table(params$shutdown_time_table)
```

Distribution of shutdown times:
```{r echo=FALSE, out.width='120%'}
knitr::include_graphics(params$shutdown_time_distrib)
```


### Missed curtailments
Missed curtailment represent situations when the reduction in rotor speed between the start and the end of the curtailment signals did not reached the "safe shutdown threshold" (`r params$safe_shutdown_threshold` rpm), indicating the turbine did not respond to the curtailment signal or did not respond correctly. Only a set of turbine was included in this analysis (see "Response time" section).

Missed curtailments:
```{r echo=FALSE}
report_table(params$curtail_missed_table)
```

### Delayed curtailments
Delayed curtailment analysis is based on a theoretical collision-course analysis. It is defined as any curtailment where the bird’s projected trajectory indicated that it could reach the rotor-swept zone before the blades slowed to the "safe shutdown threshold" (`r params$safe_shutdown_threshold` rpm). Only a set of turbine was included in this analysis (see "Response time" section).

**Curtailments falling short or exceeding**

Frequency of distances falling short or exceeding the "safe shutdown distance" (i.e. the distance at which the bird would theoretically reach the rotor-swept zone before the turbine has slowed to the "safe shutdown threshold" assuming direct flight trajectory to the rotor and the same average speed):
```{r echo=FALSE, out.width='90%'}
knitr::include_graphics(params$delayed_curtail_graph)
```

```{r echo=FALSE, out.width='120%'}
knitr::include_graphics(params$delayed_curtail_per_priority_graph)
```

**Proportion of curtailments falling short or exceeding**

Proportion of curtailments falling short/exceeding per Priority Bird species:
```{r echo=FALSE, out.width='120%'}
knitr::include_graphics(params$delayed_curtail_per_priority_prop_graph)
```


**Safe distances for each curtailment**

Distribution of calculated "safe distances" for each curtailment based on each bird average track speed and turbine shutdown time:
```{r echo=FALSE, out.width='100%'}
knitr::include_graphics(params$safe_dist_graph)
```

Safe distances per Priority Bird species:
```{r echo=FALSE, out.width='120%'}
knitr::include_graphics(params$safe_dist_per_priority_graph)
```

# 4. Coverage

### WF coverage
IDF unit system locations and indicative detection range (assuming `r params$idf_op_detection_range`m). The map below illustrates the potential detection extent and does not represent a formal on-site coverage assessment:
```{r echo=FALSE, out.width='120%'}
knitr::include_graphics(params$coverage_wf_graph)
```

Proportion of turbines covered by IDF:
```{r echo=FALSE}
report_table(params$IDF_coverage_WF_table)
```

### On-site WTG volumetric coverage - wider radius (1000m)
Analysis not available for the current report.


### On-site WTG volumetric coverage - risk radius (600m)
Analysis not available for the current report.



# 5. Biological

## Flight at risk height

Total flights at risk (Priority Bird species pooled):
```{r echo=FALSE}
report_table(params$flight_risk_table)
```

Total flights at risk per Priority Bird species:
```{r echo=FALSE}
report_table(params$flight_risk_per_sp_table)
```

## Flight height

Flight height per Priority Bird species:
```{r echo=FALSE}
report_table(params$flight_height_sp_table)
```

## Flight speed

Flight speed per Priority Bird species:
```{r echo=FALSE}
report_table(params$flight_speed_sp_table)
```


```{r echo=FALSE, out.width='120%'}
knitr::include_graphics(params$flight_height_per_sp_graph)
```


# 5. Annexes


## Missed curtailments

Missed curtailments events table:
```{r echo=FALSE}
report_table(params$missed_events_table)
```

